### 2016-04-11 paper/paper.tex
first commit

\input{headers}

\begin{abstract}

Since its creation in 2009, Bitcoin has used a hash-based proof-of-work to
generate new blocks, and create a single public ledger of transactions. The
hash-based computational puzzle employed by Bitcoin is instrumental to its
security, preventing sybill attacks and making double-spending attacks more
difficult. However, there have been concerns over the efficiency of this
proof-of-work puzzle, and alternative ``useful'' proofs have been proposed.

In this paper, we present DDoSCoin, which is a cryptocurrency with a
\emph{mallicious} proof-of-work. DDoSCoin allows miners to prove that they have
contributed to a distributed denial of service attack against a specific target.
This proof involves making a large number of TLS connections to a target server,
and using infrequent cryptographic responses as a proof.

\end{abstract}

\section{Introduction}

Cryptocurrencies rely on proofs-of-work (PoW) that
require miners to spend a large amount of effort to solve a specific puzzle,
such that once solved, allowing others to inexpensively verify the solution is a
valid one. In Bitcoin, the proof-of-work is a computational puzzle based on the
SHA256 hash function, and miners are tasked with finding a partial preimage. The
only known way to do this is to iterate over a large number of inputs to the
hash function, and check if the output hash is less than a specified target. In
simplified terms, to find an input that hashes to N bits of 0s, the miner must
perform on average $2^{N}$ hashes. However, once found, other miners and Bitcoin
nodes can verify the puzzle solution with
a single hash~\footnote{Bitcoin uses double-SHA256 in its design, but this
detail is not important for the purposes of this paper.}.

Although the proof-of-work used in Bitcoin gives it resistance to sybil attacks,
the amount of computational effort carried out collectively by its miners does
not contribute to any problems besides securing the currency from attack.
Indeed, this computational effort is substantial: As of 2016, miners
collectively perform roughly $10^{18}$ (or about $2^{60}$) hashes every
second~\cite{blockchain}.

Previously, researchers have proposed alternative cryptocurrencies (altcoins)
that aim to have more beneficial proofs-of-work~\cite{primecoin,permacoin} that
provide utility beyond securing the underlying currency. In this paper however,
we investigate going in the opposite direction, and propose an altcoin that has
a \emph{malicious} proof-of-work that is externally detrimental.

In particular, we propose a proof-of-work that allows miners to prove they have
participated in a distributed denial of service (DDoS) attack against a
particular target. Miners are incentivized to send and receive large amounts of network
traffic at the target in order to produce a valid proof-of-work. As in other
cryptocurrencies, these proofs can be inexpensively verified by others, and the
original miner can collect a reward. This reward can be sold for other
currencies (including Bitcoin or even traditional currencies), allowing botnet
owners and other attacks to directly collect revenue for their assistance
in a decentralized DDoS attack.

The malicious proof-of-work operates by having miners create a large number of
TLS connections to a target webserver, and using the server's signed responses
as a proof of connection. In modern versions of TLS, the server signs a
client-provided parameter of the connection, along with server-provided values
used in the key exchange of the connection. This allows the client to prove to
others that it has communicated with the server. In addition, the signed value
returned by the server is not predictable to the client, and is randomly
distributed. Thus, clients can use a similar trick as in Bitcoin, and only
report connections that match some rare threshold, such as the signature from
the server starts with $N$ bits of 0s. On average, it will take clients $2^{N}$
connections to produce such a proof.

Although the malicious proof-of-work only works against websites that support
TLS 1.2, as of April 2016, over 51\% of the Alexa top million websites support
this version of TLS~\cite{censys}. Furthermore, we expect this number to
increase as TLS support becomes more widespread~\cite{letsencrypt}.

\emph{Contributions}
\begin{itemize}
\item Propose a novel conceptual cryptocurrency, DDoSCoin, whose proof-of-work
incentives miners to participate in a DDoS attack, and prove they have done so.
\item Implement our proof-of-work function and evaluate its performance.
\item Discuss and estimate the impact such a cryptocurrency would have if
deployed, and outline defenses.
\end{itemize}

Section blah does blah, and Section blat describes blat.

\section{Related Work}

Ethereum
Permacoin
Primecoin
Other interesting proofs-of-work?

Botnet-as-a-service

\section{Background}

\section{DDoSCoin Design}

\section{Discussion}

-Proof of (burnt) bandwidth
-Defenses
-Target server's participation

\section{Conclusion}

{\footnotesize\balance
\bibliographystyle{plain}
\bibliography{paper}}

\end{document}

### 2016-04-21 paper/paper.tex
add design

@@
 Although the malicious proof-of-work only works against websites that support
-TLS 1.2, as of April 2016, over 51\% of the Alexa top million websites support
+TLS 1.2, as of April 2016, over 56\% of the Alexa top million websites support
 this version of TLS~\cite{censys}. Furthermore, we expect this number to
@@
 
+Miners in DDoSCoin repeatedly create connections to a TLS victim server, and
+check for a response that satisifes a target difficulty decided by the network.
+If the response satisifies this condition, then parameters of the TLS handshake
+can be published by the miner to create a new valid block.
+
+To begin, a miner generates a random 32-byte secret nonce, $N$. The miner also
+selects the latest block in the chain it is mining on, and the set of
+transactions that the miner intends to include in this block, both as is done in
+Bitcoin. The miner then takes the SHA256 hash of the previous block header, the
+Merkle root of transactions (as generated in Bitcoin), and the secret nonce $N$,
+and hashes their concatenation using SHA256 to generate the
+32-byte \texttt{client\_random} the miner will use.
+
+The miner initiates a TLSv1.2 connection with the victim server, using the
+\texttt{client\_random}, and choosing a set of cipher suites that will ensure
+the server will send a server key exchange message. This includes ephemeral
+Diffie-Hellman (DHE), and ephemeral elliptic curve Diffie-Hellman (ECDHE). We
+note that for the default cipher suite list sent by Google Chrome, over 94\%
+of TLS 1.2 servers in the Alexa top million choose a cipher suite with a server key exchange
+message~\cite{censys}, compatible with DDoSCoin.
+% https://censys.io/domain/report?q=443.https.tls.version%3A%22TLSv1.2%22&field=443.https.tls.cipher_suite.name&max_buckets=
+
+The server will respond with a server hello message, containing a 32-byte
+\texttt{server\_random}, the cipher suite that will be used, and other
+parameters that are not needed for the purposes of DDoSCoin.
+
+Next, the server sends its certificate chain, and a server key exchange message.
+The certificate chain contains the server's (signed) TLS certificate, as well as
+intermediate certificate authorities (CAs) that create a signature chain to a
+browser-trusted root CA. Inside the server's certificate is a public
+key, as well as the identity of the server (i.e. it's domain). The miner stores
+these for verification in case a block is found.
+
+In the server key exchange message, the server sends key exchange parameters
+(such as the Diffie-Hellman parameters and the ephemeral public value generated
+by the server, or the curve parameters and a public curve point in ECDHE). These
+key exchange parameters, along with the \texttt{client\_random} and
+\texttt{server\_random},  are signed by the server using its private key; this
+signature can be verified by using the public key in the certificate.
+
+Because the server key exchange signature contains the \texttt{client\_random}
+and \texttt{server\_random}, the signature value will be unpredictable to the
+client ahead of time. In other words, each signature will be a random value that
+depends on miner-provided value. Thus, it can be used as a proof-of-work in the
+following way:
+
+If the SHA256 hash of the server key exchange parameters, signature, and
+miner-chosen nonce $N$ is less than the current target difficulty, then this
+connection satisfies the proof-of-work threshold, and can be used to form the
+next block.
+
+To make a block, the miner publishes the prevoius block's hash, the transactions
+(and their Merkle root), the nonce $N$, the \texttt{server\_random} value, the
+server's certificate chain, the server key exchange parameters, and the server
+key exchange signature.
+
+\subsection{Validating Blocks}
+
+To verify that a block is valid, miners must validate several items. First, they
+must validate that the previous block hash and Merkle roots are valid, as in
+Bitcoin. Next, they must re-create the \texttt{client\_random}, by hashing the
+previous block hash, transaction Merkle root, and provided nonce. Then, they
+must validate the certificate actually belongs to a valid victim server. This is
+done by checking that the certificate chain is valid, rooted in a trusted
+certificate authority, and the domain name is in a list of acceptable victims.
+This list of valid victim domains is generated by concensus, and details for its
+generation are discussed in Section~\ref{sec:victim}.
+
+After the victim has been verified to be a valid one, the public key is used to
+verify the server key exchange signature. This signature is over the
+\texttt{client\_random}, \texttt{server\_random}, and server key exchange
+parameters.
+
+Finally, the block must be verified to meet the current target difficulty. The
+server key exchange parameters, signature, and the block's nonce ($N$) are
+hashed using SHA256, and compared to the current target difficulty. If it is
+less than the target, the block is a valid one and becomes the latest block in
+this chain.
+
+\subsection{Earlier TLS Versions}
+
+DDoSCoin is incompatible with earlier TLS (or even SSL) versions because the
+server key exchange signature does not include the \texttt{client\_random}, or
+any client-provided values. If we were to try to base a proof-of-work off of an
+earlier version of TLS, the only value that provably comes from the server (i.e.
+is signed by a key tied to the victim's identity) does not contain any
+comittments from the client about the previous block, or what transactions
+should be included in the block. If we were to accept blocks where there was
+only a server signature that met some target difficulty, any miner could steal
+another miner's found block (and the contained block reward) by changing the
+transactions and forwarding the block.
+
+If we were to somehow tie the previous block's hash and Merkle root into this
+proof, for example, by saying that the hash of the signature and a
+client-provided nonce had to be less than some target value, the proof-of-work becomes
+a computational puzzle: a miner only has to collect a single signature from
+the server, and try different nonces until the hash of signature and nonce meets
+the target difficulty.
+
+Similarly, proof-of-work target difficulties can not be based off of the
+purported shared secret that results from a connection, because the client can
+always choose different key exchange values to ensure that the resulting shared
+secret is less than than the threshold difficulty, resulting in a computational
+puzzle. Even values sent by the server---such as the Finished message that
+contains a MAC dependent on the shared secret---can be (re)computed by the client.
+
+This interesting property gives rise to an observation that with respect to
+clients, the contents of TLS connections are \emph{deniable}. That is, it is not
+possible for a client to record a TLS connection, including its chosen secrets,
+and report this to a third party in a way that cryptographically proves what the
+server says. This property has been accomplished in different more efficient ways in various
+secure messaging protocols such as Off-the-Record (OTR)~\cite{otr}.
+
+Besides TLS 1.2, there are other cryptographic protocols that have the feature
+of the server signing a client-chosen value. For example, SSH ... \TK
+
+Although not yet implemented, the TLS 1.3 proposal appears to also have ... \TK
+
+\subsection{Victim Selection}
+\label{sec:victim}
+
+If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
+incentivized to solve local challenges rather than remote ones, leading to the
+proof-of-work being a computational puzzle, rather than one based on
+participation in a network denial of service. Thus, DDoSCoin must have a way to
+agree on what victims are acceptable targets for the proofs to be considered
+valid.
+
+One simple way is to hardcode a set of victim certificates into the protocol.
+For example, DDoSCoin's published code could contain the identities of
+Facebook's servers, and only incentivize attacks against them. However, there
+are many attackers that might feel uncomfortable attacking Facebook, but would
+be willing to participate in attacks against other websites. In addition, having
+only a single or small set of websites is a risk to DDoSCoin: if those websites
+all go offline or successfully mitigate the attacks (such as by disabling TLS),
+no future DDoSCoin blocks can be mined, and the currency will stall. At this
+point, all DDoSCoins in circulation would become nearly worthless, as there
+would be no way to safely transact them.
+
+These issues lead to a few subtle requirements for choosing valid victims.
+First, there must be \emph{limits} on who is allowed to be a victim, otherwise
+miners can create local computational puzzles. At the same time, there must be
+\emph{enough} targets in order to be robust. Similarly, the list of victims must
+be \emph{flexible} in order to prevent a stalled blockchain through downed or
+propery defended servers.
+
+To address these issues, we propose two mechanisms the DDoSCoin protocol can
+employ.
+
+\subsubsection{Pay-to-DDoS}
+
+In order to allow the set of victims to be updated, DDoSCoin could allow payment
+for targetting specific servers. To accomplish this, DDoSCoin introduces a new
+payment opcode, PAY\_TO\_DDOS, that can be used in transactions subject to
+certain constraints. This opcode takes one argument: a string representing a
+domain name that the payer wishes to add to the set of victim servers. The
+transaction has no other parameters, but its value must be greater than the
+coinbase reward a miner would normally receive, and it must carry a
+non-negligble transaction fee. Once this transaction is stored in a valid block,
+the specified domain name is temporarily added to the list of allowed victims.
+The first miner to mine a block with that domain as the victim must specify the
+PAY\_TO\_DDOS transaction as an input to its coinbase transaction (with any
+arbitrary output address), and have no other coinbase transactions. In other
+words, the miner collects the value in the PAY\_TO\_DDOS transaction in lieu of
+the normal block reward.
+
+The observant reader will notice that nothing stops the payer of the
+PAY\_TO\_DDOS transaction and the miner that it goes to from being the same
+entity. Indeed, a miner could create a PAY\_TO\_DDOS transaction with a victim
+domain that only it has access to, ensuring that it will be able to mine the
+block without competition, and collect its own payment. However, this will not
+net the miner new coins (\TK beyond any transaction fees collected? But we could
+make this block contain no transactions), as the coinbase transaction is
+replaced with its own PAY\_TO\_DDOS input.
+
+\subsubsection{Alternate Proof-of-Work}
+
+-However, the victim could easily generate a new certificate; should instead
+base identity off domain rooted to valid root CAs.
+
+DDoSCoin must select a small set of victim servers to p
+
+-Miners vote (proof-of-stake-esq)
+
 \section{Discussion}
@@
 -Target server's participation
+
+\subsection{Ethical Considerations}
+¯\\\_(ツ)\_/¯
+
+Днепр kůň dominī Ngữ
 

### 2016-04-28 paper/paper.tex
hmm
¯\_(ツ)_/¯
add peercoin/proof-of-stake background

@@
 \section{Background}
+
+\subsection{Proof-of-Stake}
+
+Proof-of-Stake is an alternate way of generating new blocks in a cryptocurrency.
+In this system, blocks are ``minted'' (rather than mined) based on how much
+stake the miner has in the currency (rather than their fraction of computational
+power). Proof-of-stake assumes that the underlying cryptocurrency is already
+somewhat distributed, for example through the use of a traditional proof-of-work
+system. In this subsection, we will describe Peercoin, a currently active
+alternate cryptocurrency that employs a hybrid proof-of-work and proof-of-stake
+algorithm to mint blocks.
+
+Peercoin's proof-of-stake allows currency holders to mint new blocks based on
+how many coin-days they are able and willing to consume. ``Coin-days
+consumed'' is a measure of the product of the amount of coins spent, and the
+number of days the have not been previously spent. For example, to consume 10
+coin-days, a currency holder can spend 10 Peercoin that they have held for a
+day, or equivalently, spend 5 Peercoins that were last spent 2 days ago. Note
+that the holder can send these coins to anyone (including themselves) in order
+to consume the coin age.
+
+To mint a new block, a minter creates a special transaction (presumably one
+where the minter pays themself) where one of the
+inputs has been unspent for at least 30 days. The resulting transaction, along
+with a timestamp, must meet a certain hash target that gets easier proportional to how many
+coin-days are consumed. For example, if the current difficulty gives a minter
+consuming 100 coin-days a 1\% chance of minting a block per second, a minter
+that was able to consume 200 coin-days would have a 2\% chance per second.
+
+The input to the hash includes information about the ``aged'' transaction, as
+well as a current timestamp\footnote{In recent versions of Peercoin, the hash
+also includes a stakeModifier which is computed from recent blocks; however,
+these details are not important for our purposes}. If this hash is less than the
+current target multiplied by the number of coin-days consumed in the
+transaction, then the transaction meets the proof-of-stake difficulty and a new
+block is minted. Although this looks similar to a proof-of-work check where a
+hash is being compared to a target, here the only varying inputs are the
+long-lived (aged) input transaction, and a corse-grained timestamp with a
+resolution of 1 second. Thus, for each aged unspent transaction output they
+control, minters perform only one hash per second in order to solve the
+proof-of-stake.
+
+% hash(nStakeModifier + txPrev.block.nTime + txPrev.offset + txPrev.nTime +
+%       txPrev.vout.n + nTime) < bnTarget * nCoinDayWeight
+%
+% ss << nTimeBlockFrom << nTxPrevOffset << txPrev.nTime << prevout.n <<
+%   nTimeTx;
+% given a new tx that is going to be my "proof-of-stake" tx,
+% which has an input from prevTx (where prevTx is at least 30 days old)
+% H(nStakeModifier + txPrev.block.nTime + txPrev.offset + txPrev.nTime +
+%   txPrev.vout.n + tx.nTime)
+
+% stakeModifiers (in v0.3): you start from the block where txPrev was in,
+% and then walk forward until the first block that was made more than
+% GetStakeModifierSelectionInterval() seconds after that the block txPrev was in (about 8.8 days...)
+% If that block has the stakeModifier flag set, use its stakeModifier
+
+% Ist das system relevant?
+In Peercoin, coins cannot age beyond 90-days; coins that have not been consumed
+after 90-days are counted as 90-day-old coins. This prevents very old
+coin-holders from being able to disrupt the blockchain at a future date,
+potentially causing a large fork of the blockchain and destabalizing it.
+
+When a proof-of-stake is minted, the minter is allowed to collect a small
+subsidy proportional to the coin-age consumed in their proof-of-stake
+transaction. This serves as the only reward for a minter, as transaction fees are not
+collected by minters in Peercoin.
 
@@
 participation in a network denial of service. Thus, DDoSCoin must have a way to
-agree on what victims are acceptable targets for the proofs to be considered
+agree on what victims are acceptable targets for the proofs-of-work to be considered
 valid.
@@
 \subsection{Ethical Considerations}
-¯\\\_(ツ)\_/¯
+%¯\\\_(ツ)\_/¯
+%\symbol{2544}
+\shrug
 
-Днепр kůň dominī Ngữ
+% ¯\_(ツ)_/¯
 

### 2016-04-29 paper/paper.tex
new idea/rewrite of Pay-to-DDOS

@@
 If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
-incentivized to solve local challenges rather than remote ones, leading to the
-proof-of-work being a computational puzzle, rather than one based on
+incentivized to set up signed TLS servers locally, and focus exclusively on
+solving those challenges instead of remote ones, leading to the
+proof-of-work being a computational puzzle rather than one based on
 participation in a network denial of service. Thus, DDoSCoin must have a way to
 agree on what victims are acceptable targets for the proofs-of-work to be considered
-valid.
+valid. Similarly, it is important to focus the denial-of-service effort toward a
+single or small number of victims in order to have the most impact.
 
-One simple way is to hardcode a set of victim certificates into the protocol.
+One simple way to is to hardcode a set of victim certificates into the protocol.
 For example, DDoSCoin's published code could contain the identities of
@@
 miners can create local computational puzzles. At the same time, there must be
-\emph{enough} targets in order to be robust. Similarly, the list of victims must
-be \emph{flexible} in order to prevent a stalled blockchain through downed or
-propery defended servers.
+\emph{enough} targets in order to be robust against stalled blockchains.
+Similarly, the list of victims must be \emph{flexible} in order to allow
+removing targets as they become impractical to attack (either
+through successful attack or mitigation), and adding new ones.
 
 To address these issues, we propose two mechanisms the DDoSCoin protocol can
-employ.
+employ to allow victims to be selected by concensus.
 
@@
 
-In order to allow the set of victims to be updated, DDoSCoin could allow payment
-for targetting specific servers. To accomplish this, DDoSCoin introduces a new
-payment opcode, PAY\_TO\_DDOS, that can be used in transactions subject to
-certain constraints. This opcode takes one argument: a string representing a
-domain name that the payer wishes to add to the set of victim servers. The
-transaction has no other parameters, but its value must be greater than the
-coinbase reward a miner would normally receive, and it must carry a
-non-negligble transaction fee. Once this transaction is stored in a valid block,
-the specified domain name is temporarily added to the list of allowed victims.
-The first miner to mine a block with that domain as the victim must specify the
-PAY\_TO\_DDOS transaction as an input to its coinbase transaction (with any
-arbitrary output address), and have no other coinbase transactions. In other
-words, the miner collects the value in the PAY\_TO\_DDOS transaction in lieu of
-the normal block reward.
+In order to allow victims to be (temporarily) selected for DoS, DDoSCoin
+allows ``bounties'' for targetting specific servers. To accomplish this,
+DDoSCoin introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in
+transactions subject to certain constraints. This opcode takes two arguments in
+the output script: a
+string representing a domain name that the payer wishes to have DDoSed, and a
+target difficulty. Once this transaction is stored in a valid block, anyone can
+collect its reward by creating a connection to the specified victim server, with
+a response that meets the given target difficulty. These connections are made
+similar to the way that miners connect to victim servers to create blocks, but
+with a few important differences. First, the \texttt{client\_random} is
+generated using the PAY\_TO\_DDOS transaction ID (txid), the SHA256 hash of the
+output script the payee wants to collect the payment with, and a random nonce.
+The client then makes connections to the specified victim domain until its
+response meets the target difficulty
+(SHA256(\texttt{server\_key\_exchange\_params} || \texttt{signature} ||
+\texttt{nonce}) < target).
 
-The observant reader will notice that nothing stops the payer of the
-PAY\_TO\_DDOS transaction and the miner that it goes to from being the same
-entity. Indeed, a miner could create a PAY\_TO\_DDOS transaction with a victim
-domain that only it has access to, ensuring that it will be able to mine the
-block without competition, and collect its own payment. However, this will not
-net the miner new coins (\TK beyond any transaction fees collected? But we could
-make this block contain no transactions), as the coinbase transaction is
-replaced with its own PAY\_TO\_DDOS input.
+To collect the bounty reward, the client creates an input script that will
+satisfy the PAY\_TO\_DDOS output. This includes the parameters of the
+connection: the nonce, the \texttt{server\_random} value, the server's
+certificate chain, the server key exchange parameters, and the server key
+exchange signature. To validate the transaction, a miner must recompute the
+\texttt{client\_random} using the transaction ID of the PAY\_TO\_DDOS
+transaction, the hash of the output script in the claiming transaction, and the
+nonce. Then, the miner must verify that the certificate is valid for the
+provided domain (and rooted in a trusted CA), and that the certificate's
+signature over the server key exchange message is valid. Finally, the server
+must check that the server's response meets the target difficulty. If it does,
+then the transaction is valid and can be included in a block.
+
+There are a couple important features of this transaction. First, the reason the
+transaction ID of the PAY\_TO\_DDOS transaction is included (committed to) in
+the \texttt{client\_random} is to prevent a client from ``double-claiming''
+multiple bounty rewards with the same proof-of-DoS. Similarly, the client
+commits to the (hash of the) output script of the claiming transaction to
+prevent others from being able to swap it for their own, therby ``stealing'' the
+proof-of-DoS and collect the reward themselves. These combined allow two
+mutaully-distrusting parties to directly and safely transact currency in
+exchange for a DoS attack.
+
+% client_random = H(txid || output_script || nonce)
+
+%The transaction has no other parameters, but its value must be
+%greater than the coinbase reward a miner would normally receive, and it must
+%carry a non-negligble transaction fee. Once this transaction is stored in a
+%valid block, the specified domain name is temporarily added to the list of
+%allowed victims.  The first miner to mine a block with that domain as the victim
+%must specify the PAY\_TO\_DDOS transaction as an input to its coinbase
+%transaction (with any arbitrary output address), and have no other coinbase
+%transactions. In other words, the miner collects the value in the PAY\_TO\_DDOS
+%transaction in lieu of the normal block reward.
+%
+%The observant reader will notice that nothing stops the payer of the
+%PAY\_TO\_DDOS transaction and the miner that it goes to from being the same
+%entity. Indeed, a miner could create a PAY\_TO\_DDOS transaction with a victim
+%domain that only it has access to, ensuring that it will be able to mine the
+%block without competition, and collect its own payment. However, this will not
+%net the miner new coins (\TK beyond any transaction fees collected? But we could
+%make this block contain no transactions), as the coinbase transaction is
+%replaced with its own PAY\_TO\_DDOS input.
+
+While this new payment type allows a one-time payment for attacking a particular
+target, it cannot be used to update the long-term victim list used by miners to
+decide valid victims for blocks. Otherwise, miners could make a PAY\_TO\_DDOS
+transaction specifying their own local domain in order to always have a
+local-computation puzzle that allowed them to create new blocks in the future.
+Instead, a second method for choosing victims must be employed.
+
+%Instead, PAY\_TO\_DDOS must be a one-time only payment, allowing for the
+%creation of a single block with a payment greater than the coinbase reward. This
+%is similar to proof-of-burn, where new blocks can be created
+%by miners proving that they have destroyed a certain amount of currency. The
+%amount of currency in proof-of-burn cryptocurrencies is adjusted in the same way
+%that difficulty is adjusted for proof-of-work to maintain a constant block rate.
+%
+%\paragraph{Concerns} Because it is possible for a miner to effectively pay a
+%small fee to create a block that only they can solve quickly, PAY\_TO\_DDOS
+%could irronically create a denial of service potential for DDoSCoin. To mitigate
+%the risk of miners using PAY\_TO\_DDOS as a way to keep other miners from
+%producing blocks, the amount above the coinbase reward a PAY\_TO\_DDOS
+%transaction must pay is adjusted dynamically so that blocks that collect these
+%transactions are not able to happen frequently. Additionally, these blocks do
+%not contribute to the
 
 \subsubsection{Alternate Proof-of-Work}
+
+Proof-of-Stake to decide a delta on the victim-list.
 

### 2016-04-29 paper/paper.tex
basics of proof-of-stake ddoscoin

@@
 collected by minters in Peercoin.
+
+TODO: how does Peercoin make sure other mint?ers can't steal the coinstake
+transaction? Is it signed by the coinstake kernel, or does the coinstake kernel
+include the merkle root of transactions somehow?
 
@@
 
+In order to allow the victim list to be updated dynamically, DDoSCoin uses
+\emph{Proof-of-Stake} to let currency holders make small changes to the list of
+acceptable victim domains. Using proof-of-stake ensures that updates are only
+done by actors that already have a substantial stake in the currency, either by
+purchasing it, or by previously participating in the (DoS) mining themselves.
+
+To update the list, a currency holder ``mints'' a proof-of-stake transaction
+similar to Peercoin. First, they must hold a number of coins unspent for more
+than 30 days, and every second, hashes the aged transaction, a recent
+stake-modifier block, and a current (seconds-resolution) timestamp. If this hash
+is less than the current proof-of-stake target difficulty multiplied by the
+coin-age being consumed by this transaction, then the currency holder is allowed
+to make a new proof-of-stake block. Inside this block, the currency holder can
+make one addition to (or one deletion from) the current victim list.
+
 Proof-of-Stake to decide a delta on the victim-list.

### 2016-05-03 paper/paper.tex
add background, cleanup things

--- 2016-04-29 paper/paper.tex
@@
 \emph{mallicious} proof-of-work. DDoSCoin allows miners to prove that they have
-contributed to a distributed denial of service attack against a specific target.
-This proof involves making a large number of TLS connections to a target server,
-and using infrequent cryptographic responses as a proof.
+contributed to a distributed denial of service attack against specific target
+servers.  This proof involves making a large number of TLS connections to a
+target server, and using infrequent cryptographic responses to prove that a
+large number of connections has been made. Like proof-of-work puzzles, these
+proofs are inexpensive to verify, and can be made arbitrarily difficult to
+solve.
 
@@
 
+In this section, we review relevant basics of cryptocurrency. For a more
+detail, we refer the reader to other
+sources~\cite{bitcoin-book,bitcoin-paper,bitcoin-sok}.
+
+\subsection{Cryptocurrency}
+
+Bitcoin employs a hash-based proof-of-work protocol to construct a public ledger
+of transactions. In this protocol, miners attempt to solve a simple hash-based
+computational puzzle in order to mine blocks. Mining a block nets the miner a
+reward, and the right to specify what new (valid) transactions should be
+included in the public ledger. To mine a block, a miner must find a hash of a
+block header that is less than an adjustable target. The block header includes
+the hash of the last block found, the merkle root of the list of transactions
+the miner wants to include in this block, and a nonce. The easiest way to solve
+this puzzle is to iterate the nonce\footnote{or modify transactions, therby
+changing the merkle root} until the hash satisfies the target difficulty. Then,
+the miner publishes the found block, and miners use this block as the latest
+block.
+
 \subsection{Proof-of-Stake}
@@
 somewhat distributed, for example through the use of a traditional proof-of-work
-system. In this subsection, we will describe Peercoin, a currently active
+system. In this subsection, we will describe Peercoin, an active
 alternate cryptocurrency that employs a hybrid proof-of-work and proof-of-stake
-algorithm to mint blocks.
+algorithm to mint blocks. For more details on proof-of-stake, we refer the
+reader to the Peercoin~\cite{peercoin} and NXT~\cite{nxt} whitepapers.
 
@@
 If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
-incentivized to set up signed TLS servers locally, and focus exclusively on
-solving those challenges instead of remote ones, leading to the
-proof-of-work being a computational puzzle rather than one based on
-participation in a network denial of service. Thus, DDoSCoin must have a way to
-agree on what victims are acceptable targets for the proofs-of-work to be considered
-valid. Similarly, it is important to focus the denial-of-service effort toward a
-single or small number of victims in order to have the most impact.
+incentivized to set up their own TLS servers locally, and focus exclusively on
+``attacking'' those servers instead of remote ones. Since the miner would have
+access to the private key for that server, they would not be required to even
+create network connections, leading to the proof-of-work being a computational
+puzzle rather than one based on participation in a network denial of service.
+To prevent this, DDoSCoin must have a way to agree on what victims are
+acceptable targets for the proofs-of-work to be considered valid. Similarly, it
+is important to focus the denial-of-service effort toward a single or small
+number of victims in order to have the most impact.
 
-One simple way to is to hardcode a set of victim certificates into the protocol.
-For example, DDoSCoin's published code could contain the identities of
-Facebook's servers, and only incentivize attacks against them. However, there
-are many attackers that might feel uncomfortable attacking Facebook, but would
-be willing to participate in attacks against other websites. In addition, having
-only a single or small set of websites is a risk to DDoSCoin: if those websites
-all go offline or successfully mitigate the attacks (such as by disabling TLS),
-no future DDoSCoin blocks can be mined, and the currency will stall. At this
-point, all DDoSCoins in circulation would become nearly worthless, as there
-would be no way to safely transact them.
+One simple solution is to hardcode a set of victim certificates into the
+protocol.  For example, DDoSCoin's published code could contain the identities
+of Facebook's servers and domains, and only allow and incentivize attacks
+against them. However, there are many attackers that might feel uncomfortable
+attacking Facebook, but would be willing to participate in attacks against other
+websites. In addition, having only a single or small set of victim websites is a
+risk to DDoSCoin: if those websites all go offline or successfully mitigate the
+attacks (such as by disabling TLS), no future DDoSCoin blocks can be mined, and
+the currency will stall. At this point, all DDoSCoins in circulation would
+become nearly worthless, as there would be no way to safely transact them.
 
@@
 removing targets as they become impractical to attack (either
-through successful attack or mitigation), and adding new ones.
+through successful attack or mitigation), and adding new ones to take their
+place.
 
@@
 
-In order to allow victims to be (temporarily) selected for DoS, DDoSCoin
-allows ``bounties'' for targetting specific servers. To accomplish this,
-DDoSCoin introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in
-transactions subject to certain constraints. This opcode takes two arguments in
-the output script: a
-string representing a domain name that the payer wishes to have DDoSed, and a
-target difficulty. Once this transaction is stored in a valid block, anyone can
-collect its reward by creating a connection to the specified victim server, with
-a response that meets the given target difficulty. These connections are made
-similar to the way that miners connect to victim servers to create blocks, but
-with a few important differences. First, the \texttt{client\_random} is
-generated using the PAY\_TO\_DDOS transaction ID (txid), the SHA256 hash of the
-output script the payee wants to collect the payment with, and a random nonce.
-The client then makes connections to the specified victim domain until its
-response meets the target difficulty
+In order to allow victims to be (temporarily) selected for DoS, DDoSCoin allows
+``bounties'' for targetting specific servers. To accomplish this, DDoSCoin
+introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in transactions
+subject to certain constraints. This opcode takes two arguments in an output
+script: a string representing a domain name that the payer wishes to have
+DDoSed, and a target difficulty corresponding to the amount of connections the
+payer wishes to be made. Once this transaction is stored in a valid block,
+anyone can collect its reward by creating a connection to the specified victim
+server and obtaining a response that meets the given target difficulty. These
+connections are made similar to the way that miners connect to victim servers to
+create blocks, but with a few important differences. First, the
+\texttt{client\_random} is generated using the PAY\_TO\_DDOS transaction ID
+(txid), the SHA256 hash of the output script the payee wants to collect the
+payment with, and a random nonce.  The client then makes connections to the
+specified victim domain until it gets a response that meets the target
+difficulty specified by the PAY\_TO\_DDOS transaction.
 (SHA256(\texttt{server\_key\_exchange\_params} || \texttt{signature} ||
@@
 multiple bounty rewards with the same proof-of-DoS. Similarly, the client
-commits to the (hash of the) output script of the claiming transaction to
+commits to (a hash of) the output script of the claiming transaction to
 prevent others from being able to swap it for their own, therby ``stealing'' the
-proof-of-DoS and collect the reward themselves. These combined allow two
+proof-of-DoS and collect the reward themselves. These properties combined allow two
 mutaully-distrusting parties to directly and safely transact currency in
-exchange for a DoS attack.
+exchange for a specified-amount of work in a DoS attack.
+
+% Maybe move this to discussion....
+Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
+the collector that by the time they complete their DoS attack, someone else will
+have collected the payment. In addition, a potential victim website could
+disincentivze attacks by submitting PAY\_TO\_DDOS transactions that they can
+quickly solve locally. This would cause attackers to try to connect to them, and
+eventually even collect a response that meets the target difficulty. However,
+when the attacker went to publish this to collect the reward, the victim could
+publish their proof, essentially double-spending the PAY\_TO\_DDOS transaction.
+With some probability, the victim's transaction will ``win'' and prevent the
+attacker from collecting the reward. Over the long term, attackers may be wary
+of attacking such targets, and instead require higher payouts for attacking them
+to cover such risks.
 
@@
 
-Proof-of-Stake to decide a delta on the victim-list.
+In order to allow the victim list to be updated dynamically, DDoSCoin uses
+\emph{Proof-of-Stake} to let currency holders make small changes to the list of
+acceptable victim domains. Using proof-of-stake ensures that updates are only
+done by actors that already have a substantial stake in the currency, either by
+purchasing it or by previously participating in the (DoS) mining themselves.
 
--However, the victim could easily generate a new certificate; should instead
-base identity off domain rooted to valid root CAs.
+To update the list, a currency holder ``mints'' a proof-of-stake transaction
+similar to Peercoin. First, they must hold a number of coins that have been
+unspent for more than 30 days. After the 30 days have passed, each second the
+minter
+hashes the aged transaction, a recent stake-modifier block, and a current
+(seconds-resolution) timestamp. If this hash is less than the current
+proof-of-stake target difficulty multiplied by the coin-age being consumed in
+this transaction, then the currency holder is allowed to make a new
+proof-of-stake block. Inside this block, the currency holder can make one
+addition to (or one deletion from) the current victim list.
 
-DDoSCoin must select a small set of victim servers to p
+Proof-of-stake blocks contains no coinbase or coinstake reward, and transaction
+fees are not collected. Thus, there is no direct short-term monetary incentive
+to produce such a block. The intention is that this will encourage only those
+with a vested interest in the long-term success of DDoSCoin to participate in
+updating the victim list.
 
--Miners vote (proof-of-stake-esq)
+After this block has been published, miners must wait until 10 proof-of-DoS
+(non-proof-of-stake) blocks have been mined before the specified delta to the
+change list is applied. This discourages malicious miners from forking the chain
+at an earlier block with a proof-of-stake block adding their local domain to the
+victim list, and immediately mining blocks on top of it to catch up to the main
+chain.
+
+%Proof-of-Stake to decide a delta on the victim-list.
+
+%-However, the victim could easily generate a new certificate; should instead
+%base identity off domain rooted to valid root CAs.
+
+%DDoSCoin must select a small set of victim servers to p
+
+%-Miners vote (proof-of-stake-esq)
 

### 2016-05-08 paper/figures.tex
add btc-tx

\newcommand{\FigTx}{
\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.9\textwidth,trim={0 6.5cm 1cm 0},clip]{btc-transaction.pdf}
    \caption{Standard Bitcoin transaction script. Transaction \#10 spends \#9 by providing a
            valid input script that when prepended to Transaction \#9's output script,
            executes to produce a valid output. The output script stores a hash of a
            public key (verified using the OP\_DUP OP\_HASH160 and OP\_EQUALVERIFY opcodes),
            and requires a valid signature over the spending transaction (verified via
            OP\_CHECKSIG).}
\end{figure*}
}

### 2016-05-08 paper/paper.tex
add btc-tx

@@
 \input{headers}
+\input{figures}
 
@@
 incentives miners to participate in a DDoS attack, and prove they have done so.
+\item Describe a way for target victims to be chosen by consensus.
 \item Implement our proof-of-work function and evaluate its performance.
@@
 
-In this section, we review relevant basics of cryptocurrency. For a more
+In this section, we review relevant basics of cryptocurrency. For more
 detail, we refer the reader to other
@@
 \subsection{Cryptocurrency}
+
+\FigTx
 
@@
 block.
+
+Each block commits to a set of transactions, which each must be valid for the
+block to be considered valid. Transactions in Bitcoin are scripts, and each new
+transactions specifies an \emph{output script} that must be satisfied in order
+to be spent. For example, an output script might specify that it requires a
+spending transaction to provide a valid signature, with the output script
+specifying the public key to validate it with.
 

### 2016-05-09 paper/figures.tex
add ddoscoin overview figure

@@
     \includegraphics[width=0.9\textwidth,trim={0 6.5cm 1cm 0},clip]{btc-transaction.pdf}
-    \caption{Standard Bitcoin transaction script. Transaction \#10 spends \#9 by providing a
+    \caption{\textbf{Standard Bitcoin transaction script}\,--\, %
+            Transaction \#10 spends \#9 by providing a
             valid input script that when prepended to Transaction \#9's output script,
@@
             OP\_CHECKSIG).}
+    \label{fig:bitcoin-tx}
 \end{figure*}
 }
+
+\newcommand{\FigOverview}{
+\begin{figure*}[ht]
+    \centering
+    \includegraphics[width=0.9\textwidth,trim={0 9.5cm 9.2cm 0},clip]{ddoscoin-overview.pdf}
+    \caption{\textbf{DDoSCoin Design}\,--\, %
+    DDoSCoin miners make repeated connections to a victim server running TLSv1.2
+(1). In the handshake, the miner commits to the previous block, a transaction
+merkle root, and a secret nonce. Eventually the victim server will respond with
+a signed message that meets the current proof-of-DDoS target, and the miner can
+create a new block (2) that includes this proof. Victim targets can be selected
+in one of two ways. First, participants can pay into bounties for specific
+victims (3), which can be redeemed by anyone in a special PAY\_TO\_DDOS
+transaction (5) if they can provide a similar proof-of-DDoS. Second, the list of
+valid victims that blocks can be mined for can be updated by proof-of-stake
+blocks (4).}
+    \label{fig:ddoscoin-overview}
+\end{figure*}
+}

### 2016-05-09 paper/paper.tex
add ddoscoin overview figure

@@
 spending transaction to provide a valid signature, with the output script
-specifying the public key to validate it with.
+specifying the public key to validate it with. To spend such a transaction
+requires creating a new transaction that references the previous one, and
+provides an input (scriptSig) that ``solves'' the previous transactions' output
+(scriptPubKey); in this case, a valid signature over the new transaction. This
+new transaction can then specify a new output (scriptPubKey) for these coins.
+Figure~\ref{fig:bitcoin-tx} shows an example of a standard Bitcoin transaction
+script.
 
@@
 \section{DDoSCoin Design}
+
+\FigOverview
 

### 2016-05-09 paper/paper.tex
add some references

@@
 TLS 1.2, as of April 2016, over 56\% of the Alexa top million websites support
-this version of TLS~\cite{censys}. Furthermore, we expect this number to
-increase as TLS support becomes more widespread~\cite{letsencrypt}.
+this version of TLS according to censys.io~\cite{censys}. Furthermore, we
+expect this number to increase as TLS support becomes more
+widespread~\cite{letsencrypt}.
 

### 2016-05-13 paper/paper.tex
add some conclusion, fixup references, more detail on tls 1.3 and ssh

@@
 collectively perform roughly $10^{18}$ (or about $2^{60}$) hashes every
-second~\cite{blockchain}.
+second~\cite{blockchain-hashrate}.
 
@@
 \end{itemize}
+%TODO: remove this last one?
 
-Section blah does blah, and Section blat describes blat.
+%Section blah does blah, and Section blat describes blat.
 
@@
 
-Ethereum
-Permacoin
-Primecoin
-Other interesting proofs-of-work?
+Many alternate cryptocurrency protocols (alt-coins) have been proposed since the
+creation of Bitcoin. Although none have yet eclipsed the popularity of Bitcoin,
+many alt-coins have interesting innovations, often in the form of alternate
+proof-of-work. For example, Litecoin uses scrypt in place of SHA256 in its
+proof-of-work, with the intention of being ``ASIC-resistant'' in order to allow
+anyone to mine competatively with only a CPU~\cite{litecoin}.
 
-Botnet-as-a-service
+Permacoin is a proposed alt-coin that uses a novel
+\emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
+resources solving a useless proof-of-work puzzle (as in Bitcoin), miners are
+instead incentivzed to store parts of a large agreed-upon file. In order to be
+competitive in Permacoin, miners prove that they can retreive an assigned
+portion of the file.
+
+In Primecoin, miners search for special chains of prime
+numbers~\cite{primecoin}. Although Primecoin has found several large Cunningham
+and bi-twin chains, it remains unclear if such primes have any practical use.
+
+Although Bitcoin uses a scripting language for transactions (see
+Section~\ref{sec:scripting}), the allowed operations are very
+limited~\cite{bitcoin-paper}. Ethereum allows transactions to be
+\emph{programmable contracts}, whereby a programmer can specify in a custom
+scripting language arbitrary logic, including conditional payments or
+fee-collection. While the Ethereum Virtual Machine (EVM) that executes these
+contracts does not provide external network access to the scripts, it could
+still be used to implement some parts of DDoSCoin. For example, it is possible
+to create an Ethereum contract that pays a bounty to anyone that can provide a
+proof-of-DDoS for a specified target. This would effectively accomplish the same
+outcome as PAY\_TO\_DDOS (described in Section~\ref{sec:pay-to-ddos}), and
+implementing DDoSCoin's proof-of-DDoS verification.
+
+%Other interesting proofs-of-work?  Botnet-as-a-service?
 
@@
 \subsection{Cryptocurrency}
-
+\label{sec:scripting}
 \FigTx
@@
 
-The miner initiates a TLSv1.2 connection with the victim server, using the
-\texttt{client\_random}, and choosing a set of cipher suites that will ensure
-the server will send a server key exchange message. This includes ephemeral
-Diffie-Hellman (DHE), and ephemeral elliptic curve Diffie-Hellman (ECDHE). We
-note that for the default cipher suite list sent by Google Chrome, over 94\%
-of TLS 1.2 servers in the Alexa top million choose a cipher suite with a server key exchange
-message~\cite{censys}, compatible with DDoSCoin.
+The miner initiates a TLS version 1.2~\cite{rfc5246} connection with the victim
+server, using the \texttt{client\_random}, and choosing a set of cipher suites
+that will ensure the server will send a server key exchange message. This
+includes ephemeral Diffie-Hellman (DHE), and ephemeral elliptic curve
+Diffie-Hellman (ECDHE). We note that for the default cipher suite list sent by
+Google Chrome, over 94\% of TLS 1.2 servers in the Alexa top million choose a
+cipher suite with a server key exchange message~\cite{censys}, compatible with
+DDoSCoin.
 % https://censys.io/domain/report?q=443.https.tls.version%3A%22TLSv1.2%22&field=443.https.tls.cipher_suite.name&max_buckets=
@@
 server key exchange signature does not include the \texttt{client\_random}, or
-any client-provided values. If we were to try to base a proof-of-work off of an
-earlier version of TLS, the only value that provably comes from the server (i.e.
+any client-provided values. In earlier versions, the only value that provably comes from the server (i.e.
 is signed by a key tied to the victim's identity) does not contain any
@@
 clients, the contents of TLS connections are \emph{deniable}. That is, it is not
-possible for a client to record a TLS connection, including its chosen secrets,
+possible for a client to record a TLS connection (including its chosen secrets)
 and report this to a third party in a way that cryptographically proves what the
@@
 
-Besides TLS 1.2, there are other cryptographic protocols that have the feature
-of the server signing a client-chosen value. For example, SSH ... \TK
+Besides TLS 1.2, there are other cryptographic protocols that include the server
+signing a client-chosen value. For example, the SSH protocol key exchange
+involves the server signing a hash over the previous handshake messages,
+including the client-provided identification (version) string, and
+Diffie-Hellman public value~\cite{rfc4253}. Either of these fields could be used
+to encode the necessary commitments (previous block, merkle root, and nonce)
+used in DDoSCoin.  However, SSH server identities are generally not signed by a
+trusted party, making verification that a miner has communicated with a
+particular server more complicated.  Nonetheless, identities in an SSH-based
+DDoSCoin could be based off of the server's host key, rather than a domain in a
+CA-signed certificate.
 
-Although not yet implemented, the TLS 1.3 proposal appears to also have ... \TK
+Although not yet implemented, the current TLS 1.3 proposal appears to also have the
+property of the server signing messages sent by the client. In particular, the
+Certificate Verify message includes a signature from the server over essentially
+all prior handshake messages, including the Client Hello that contains the
+\texttt{client\_random}. Thus, DDoSCoin could be used against TLS 1.3
+servers with only minor modifications.
 
@@
 
+\subsection{Implementation}
+
+To evaluate its performance, we implement our proof-of-DDoS function in 570
+lines of C. Our mining code uses libevent~\cite{libevent} and
+OpenSSL~\cite{openssl}.
+
+From wifi: 100 concurrent conns, 10k connections total in 53 seconds, 500KB/s
+roughly (no CPU load)
+
+TODO: measure from CU...or to a local server?
+
 \section{Discussion}
@@
 
+\subsection{Defenses}
+
+There are several methods victim websites can use to defend themselves from
+DDoSCoin miners. First, websites can simply disable TLS 1.2 entirely, and only
+support earlier versions such as TLS 1.0~\cite{rfc2246} and TLS
+1.1~\cite{rfc4346}. While older versions of
+TLSv1.0 clients may still be vulnerable to the BEAST attack~\cite{beast}, most
+modern clients have mitigations for this attack, and it likely remains the
+safest short-term defense against DDoSCoin. The downside of disabling support
+for TLSv1.2 is losing the ability to negotiate authenticated encryption cipher
+modes with clients, which may decrease performance of implementations that have
+hardware acceleration for such modes.
+
+Alternatively, web servers can disable cipher modes that involve signatures from
+the server. This would remove support for forward secure cipher suites, meaning
+that as long as the server's private key is accessible, any previously recorded
+TLS connections can be decrypted. We note that the current drafts of TLSv1.3
+propose to remove non-forward secure cipher suites entirely, possibly making it
+more difficult to defend against DDoSCoin in TLSv1.3.
+
+Websites could also attempt to thwart DDoSCoin by participating in the mining
+themselves. Because the victim website will have local access to its private
+key, they will have an advantage over remote clients. With this advantage, the
+victim might be able to mine enough DDoSCoins to mint a proof-of-stake block
+that removes itself from the list.
+
+Finally, websites could attempt to go after mining operations legally:
+Publishing a proof-of-DDoS block in the DDoSCoin blockchain may reveal intent to
+bring down a service for financial profit. If the victim webserver is able to
+log the traffic they receive, they can discover the IP address of the party
+given a published proof-of-DDoS block. However, as many attackers may use proxies,
+botnets, or bullet-proof hosting to carry out their attacks, finding an
+attacker's IP address may not be sufficient for legal action.
+
 \section{Conclusion}
+
+In this paper, we have presented a proof-of-DDoS, whereby cryptocurrency miners
+can prove their involvement in sending a large amount of requests to a specified
+victim webserver. Proof-of-DDoS can be used to replace proof-of-work in a
+cryptocurrency setting, provided that there is consensus around what victims are
+valid targets. Our conceptual alt-coin, DDoSCoin, provides such a concensus
+through two mechanisms: PAY\_TO\_DDOS, whereby a bounty can be set for DDoSing a
+given victim domain, and proof-of-stake updates to the list of valid victims.
+
+The relatively-short history of cryptocurrency is an exciting one, litered with
+mystery
 

### 2016-05-13 paper/paper.tex
add torpath ref, (need text) and finish conclusion

@@
 and bi-twin chains, it remains unclear if such primes have any practical use.
+
+TorPath~\cite{torpath} ... \TK
 
@@
 
-The relatively-short history of cryptocurrency is an exciting one, litered with
-mystery
+Cryptocurrency inovation continues to produce new and useful proof-of-work
+replacements. Still, proving access to arbitrary resources remains a difficult
+challenge. In this direction, DDoSCoin delivers a novel technique for proving
+the use of bandwidth to a (potentially unwilling) target domain. We hope that
+this work encourages others to discover and inovate on novel proof-of-resource
+puzzles.
 

### 2016-05-13 miner.c
remove printing every connection

@@ -136,9 +136,8 @@ void handle_cert(struct conn_state *st)
 
 int satisfies_proof_of_work(uint8_t *server_dh_params, size_t server_dh_params_len,
                             uint8_t *sig, size_t sig_len,
-                            uint8_t *nonce, uint8_t *difficulty)
+                            uint8_t *nonce, uint8_t *difficulty, uint8_t *digest)
 {
-    uint8_t digest[SHA256_DIGEST_LENGTH];
     SHA256_CTX ctx;
     SHA256_Init(&ctx);
     SHA256_Update(&ctx, server_dh_params, server_dh_params_len);
@@ -146,7 +145,6 @@ int satisfies_proof_of_work(uint8_t *server_dh_params, size_t server_dh_params_l
     SHA256_Update(&ctx, nonce, 32);
     SHA256_Final(digest, &ctx);
 
-    print_hex("   difficulty: ", digest, SHA256_DIGEST_LENGTH);
     int i;
     for (i=0; i<SHA256_DIGEST_LENGTH; i++) {
         if (digest[i] < difficulty[i]) {
@@ -194,6 +192,7 @@ void handle_keyx(struct conn_state *st)
 {
     struct evbuffer *input = bufferevent_get_input(st->bev);
     size_t keyx_len = get_tls_record(input, &st->keyx_raw);
+    uint8_t digest[SHA256_DIGEST_LENGTH];
 
     if (keyx_len == 0) {
         return;
@@ -208,11 +207,12 @@ void handle_keyx(struct conn_state *st)
 
     // Check if it passes the test
     if (satisfies_proof_of_work(st->skeyx.server_dh_params, st->skeyx.server_dh_params_len,
-                            st->skeyx.sig, st->skeyx.sig_len, st->nonce, st->conf->difficulty)) {
+                            st->skeyx.sig, st->skeyx.sig_len, st->nonce, st->conf->difficulty, digest)) {
 
         struct block new_block;
         make_block_from_state(st, &new_block);
         printf("Winner!\n");
+        print_hex("   difficulty: ", digest, SHA256_DIGEST_LENGTH);
         print_hex("nonce: ", st->nonce, 32);
         print_hex("server_random: ", st->shello.random, 32);
         print_hex("server_dh_params: ", st->skeyx.server_dh_params, st->skeyx.server_dh_params_len);
[…]

### 2016-05-13 miner.c
add comment about sysctl for more reliable connection reuse

@@ -316,6 +316,7 @@ void new_connection(struct config *conf)
                                    sizeof(conf->sin)) < 0) {
 
         perror("socket connected failed: ");
+        printf("Run `sudo sysctl -w net.ipv4.tcp_tw_recycle=1`\n");
         cleanup(st);
     }
 

### 2016-05-13 miner.c
print status every second

@@ -46,6 +46,7 @@ struct config {
     uint8_t     difficulty[32];
 
     size_t      num_connections;
+    size_t      last_connections;
 
     // TODO: remove
     RSA         *public_key;
@@ -333,6 +334,14 @@ void fetcher(struct config *conf, int conns)
     }
 }
 
+void print_status(evutil_socket_t fd, short what, void *arg)
+{
+    struct config *conf = arg;
+
+    printf("%d/sec\n", (conf->num_connections - conf->last_connections));
+    conf->last_connections = conf->num_connections;
+}
+
 int main()
 {
     struct config conf;
@@ -369,8 +378,12 @@ int main()
 
     conf.base = event_base_new();
 
-    fetcher(&conf, 1000);
 
+    struct timeval one_sec = {1,0};
+    struct event *status_ev = event_new(conf.base, -1, EV_PERSIST, print_status, &conf);
+    event_add(status_ev, &one_sec);
+
+    fetcher(&conf, 1000);
     event_base_dispatch(conf.base);
 
     return 0;

### 2016-05-13 paper/figures.tex
add data and figure

@@
 }
+
+\newcommand{\FigEval}{
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.9\linewidth]{../data/times.pdf}
+    \caption{\textbf{DDoSCoin effect}\,--\, %
+    We set up a quad-core nginx HTTPS server on a local network, and used Apache
+benchmark (ab) to measure page load times under normal conditions (no DDoSCoin
+miner running) and with a single DDoSCoin instance. DDoSCoin increases the
+average page-load time 6-fold from 43ms to over 291ms.}
+    \label{fig:eval}
+\end{figure}
+}

### 2016-05-13 paper/paper.tex
add data and figure

@@
 
-To evaluate its performance, we implement our proof-of-DDoS function in 570
-lines of C. Our mining code uses libevent~\cite{libevent} and
-OpenSSL~\cite{openssl}.
+\FigEval
 
-From wifi: 100 concurrent conns, 10k connections total in 53 seconds, 500KB/s
-roughly (no CPU load)
+To evaluate the performance and effectiveness of DDoSCoin, we implement our
+proof-of-DDoS function in 582 lines of C. Our mining code uses
+libevent~\cite{libevent} and OpenSSL~\cite{openssl} to create concurrent
+connections toward a specific target, testing each response to see if it
+satisfies a hard-coded proof-of-DDoS target difficulty.
 
-TODO: measure from CU...or to a local server?
+We tested our proof-of-DDoS function (miner) against a quad-core server under
+our control, running nginx and connected to our attacker over a local Gigibit
+network. When running our miner, the CPU consumption of the server quickly
+reaches 100\% utilization on all 4 cores, while the attacker only requires
+approximately 30\% on a single core. This produces over 3000 TLS connections per
+second, and slowing responses to the server by more than a factor of 6 (see
+Figure~\ref{fig:eval}).
 
+\if0
 \section{Discussion}
@@
 \subsection{Defenses}
+\fi
+\section{Defenses}
 

### 2016-05-13 paper/paper.tex
s/TLSv/TLS /

@@
 
-TODO: how does Peercoin make sure other mint?ers can't steal the coinstake
-transaction? Is it signed by the coinstake kernel, or does the coinstake kernel
-include the merkle root of transactions somehow?
+%TODO: how does Peercoin make sure other mint?ers can't steal the coinstake
+%transaction? Is it signed by the coinstake kernel, or does the coinstake kernel
+%include the merkle root of transactions somehow?
 
@@
 \subsubsection{Pay-to-DDoS}
+
+\label{sec:pay-to-ddos}
 
@@
 1.1~\cite{rfc4346}. While older versions of
-TLSv1.0 clients may still be vulnerable to the BEAST attack~\cite{beast}, most
+TLS 1.0 clients may still be vulnerable to the BEAST attack~\cite{beast}, most
 modern clients have mitigations for this attack, and it likely remains the
 safest short-term defense against DDoSCoin. The downside of disabling support
-for TLSv1.2 is losing the ability to negotiate authenticated encryption cipher
+for TLS 1.2 is losing the ability to negotiate authenticated encryption cipher
 modes with clients, which may decrease performance of implementations that have
@@
 that as long as the server's private key is accessible, any previously recorded
-TLS connections can be decrypted. We note that the current drafts of TLSv1.3
+TLS connections can be decrypted. We note that the current drafts of TLS 1.3
 propose to remove non-forward secure cipher suites entirely, possibly making it
-more difficult to defend against DDoSCoin in TLSv1.3.
+more difficult to defend against DDoSCoin in TLS 1.3.
 

### 2016-05-15 paper/figures.tex
first edits pass

@@
     DDoSCoin miners make repeated connections to a victim server running TLSv1.2
-(1). In the handshake, the miner commits to the previous block, a transaction
+\numcircledmod{1}. In each handshake, the miner commits to the previous block, a transaction
 merkle root, and a secret nonce. Eventually the victim server will respond with
-a signed message that meets the current proof-of-DDoS target, and the miner can
-create a new block (2) that includes this proof. Victim targets can be selected
-in one of two ways. First, participants can pay into bounties for specific
-victims (3), which can be redeemed by anyone in a special PAY\_TO\_DDOS
-transaction (5) if they can provide a similar proof-of-DDoS. Second, the list of
+a signed message that meets the current proof-of-DDoS target difficulty, and the miner can
+create a new block \numcircledmod{2} that includes this proof. Victim targets can be selected
+in two ways: First, participants can pay into one-time bounties for specific
+victims \numcircledmod{3}, which can be redeemed by anyone in a special PAY\_TO\_DDOS
+transaction \numcircledmod{5} if they can provide a similar proof-of-DDoS against that victim. Second, the list of
 valid victims that blocks can be mined for can be updated by proof-of-stake
-blocks (4).}
+blocks \numcircledmod{4}.}
     \label{fig:ddoscoin-overview}
@@
 \newcommand{\FigEval}{
-\begin{figure}[ht]
+\begin{figure}[t]
     \centering

### 2016-05-15 paper/paper.tex
first edits pass

@@
 
-Cryptocurrencies rely on proofs-of-work (PoW) that
-require miners to spend a large amount of effort to solve a specific puzzle,
-such that once solved, allowing others to inexpensively verify the solution is a
-valid one. In Bitcoin, the proof-of-work is a computational puzzle based on the
-SHA256 hash function, and miners are tasked with finding a partial preimage. The
-only known way to do this is to iterate over a large number of inputs to the
-hash function, and check if the output hash is less than a specified target. In
-simplified terms, to find an input that hashes to N bits of 0s, the miner must
-perform on average $2^{N}$ hashes. However, once found, other miners and Bitcoin
-nodes can verify the puzzle solution with
-a single hash~\footnote{Bitcoin uses double-SHA256 in its design, but this
-detail is not important for the purposes of this paper.}.
+Cryptocurrencies rely on proofs-of-work (PoW) that require miners to spend a
+large amount of effort to solve a specific puzzle.  Solutions to these puzzles,
+on the other hand, are designed to be inexpensive to verify. In Bitcoin, the
+proof-of-work is a computational puzzle based on the SHA256 hash function, and
+miners are tasked with finding a partial preimage. The best way to do this is to
+iterate over a large number of inputs to the hash function, and check if the
+output hash satisifes the partial preimage target. In simplified terms, to find
+an input that hashes to N bits of 0s, the miner must perform on average $2^{N}$
+hashes. Once such an input is found, other miners and Bitcoin nodes can verify the
+puzzle solution with a single hash~\footnote{Bitcoin uses double-SHA256 in its
+design, but this detail is not important for the purposes of this paper.}.
 
@@
 the amount of computational effort carried out collectively by its miners does
-not contribute to any problems besides securing the currency from attack.
+not contribute to any useful problems besides securing the currency from attack.
 Indeed, this computational effort is substantial: As of 2016, miners
@@
 
-Previously, researchers have proposed alternative cryptocurrencies (altcoins)
-that aim to have more beneficial proofs-of-work~\cite{primecoin,permacoin} that
-provide utility beyond securing the underlying currency. In this paper however,
-we investigate going in the opposite direction, and propose an altcoin that has
-a \emph{malicious} proof-of-work that is externally detrimental.
+Many see this distributed computation as a collosal waste of CPU resources, and researchers have proposed
+alternative cryptocurrencies (altcoins) that aim to have more beneficial
+proofs-of-work~\cite{primecoin,permacoin} that provide utility beyond securing
+the underlying currency, such as finding chains of large primes or
+proving the archive of data. In this paper however, we investigate going in the
+opposite direction, and propose an altcoin that has a \emph{malicious}
+proof-of-work that is externally detrimental.
 
@@
 
-The malicious proof-of-work operates by having miners create a large number of
+The malicious ``proof-of-DDoS'' operates by having miners create a large number of
 TLS connections to a target webserver, and using the server's signed responses
@@
 
-Although the malicious proof-of-work only works against websites that support
+Although the malicious proof-of-DDoS only works against websites that support
 TLS 1.2, as of April 2016, over 56\% of the Alexa top million websites support
-this version of TLS according to censys.io~\cite{censys}. Furthermore, we
+this version of TLS~\cite{censys}. Furthermore, we
 expect this number to increase as TLS support becomes more
 widespread~\cite{letsencrypt}.
+
+Using our proof-of-DDoS, we conceptualize a cryptocurrency that uses it, which
+we call \emph{DDoSCoin}. In addition to using proof-of-DDoS, DDoSCoin allows
+miners to select the victim servers by concensus using a proof-of-stake
+protocol. Rather than specify a single website or static list that DDoSCoin
+miners target, choosing them by concensus allows the choice of who is attacked
+to be made collectively and fairly by DDoSCoin participants.
 
@@
 \item Propose a novel conceptual cryptocurrency, DDoSCoin, whose proof-of-work
-incentives miners to participate in a DDoS attack, and prove they have done so.
-\item Describe a way for target victims to be chosen by consensus.
-\item Implement our proof-of-work function and evaluate its performance.
-\item Discuss and estimate the impact such a cryptocurrency would have if
-deployed, and outline defenses.
+incentives miners to participate in a DDoS attack, and allows them prove they have done so.
+\item Describe a way for target victims to be chosen by consensus of its
+participants.
+\item Implement our proof-of-work function and evaluate its performance and
+impact.
+\item Discuss several defenses against such a cryptocurrency that potential
+victims can employ.
 \end{itemize}
-%TODO: remove this last one?
 
@@
 
-Many alternate cryptocurrency protocols (alt-coins) have been proposed since the
+Many alternate cryptocurrency protocols (altcoins) have been proposed since the
 creation of Bitcoin. Although none have yet eclipsed the popularity of Bitcoin,
-many alt-coins have interesting innovations, often in the form of alternate
+many altcoins have interesting innovations, often in the form of alternate
 proof-of-work. For example, Litecoin uses scrypt in place of SHA256 in its
@@
 
-Permacoin is a proposed alt-coin that uses a novel
+Permacoin is a proposed altcoin that uses a novel
 \emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
@@
 
-TorPath~\cite{torpath} ... \TK
+TorPath proposes a proof-of-bandwidth altcoin that incentivizes users to
+participate in the Tor Network~\cite{torpath}. However, it relies on a set of
+semi-trusted centralized servers to assign Tor circuits to clients. It is also
+succeptible to collusion and sybil attacks by participants, however many of
+these attacks are outside the threat model of TorPath as it requires performing
+those attacks against the underlying Tor network. In contrast, DDoSCoin does not
+require any centralized parties for the proof-of-DDoS, besides trusting existing
+certificate authorities to validate domains.
 
@@
 transactions specifies an \emph{output script} that must be satisfied in order
+for the coins
 to be spent. For example, an output script might specify that it requires a
@@
 power). Proof-of-stake assumes that the underlying cryptocurrency is already
-somewhat distributed, for example through the use of a traditional proof-of-work
-system. In this subsection, we will describe Peercoin, an active
-alternate cryptocurrency that employs a hybrid proof-of-work and proof-of-stake
-algorithm to mint blocks. For more details on proof-of-stake, we refer the
-reader to the Peercoin~\cite{peercoin} and NXT~\cite{nxt} whitepapers.
+somewhat distributed, for example through prior use of a traditional
+proof-of-work system. There are several variants on proof-of-stake; in this
+subsection, we will describe Peercoin, an active alternate cryptocurrency that
+employs a hybrid proof-of-work and proof-of-stake algorithm to mint blocks. For
+more details on proof-of-stake, we refer the reader to the
+Peercoin~\cite{peercoin} and NXT~\cite{nxt} whitepapers.
 
 Peercoin's proof-of-stake allows currency holders to mint new blocks based on
-how many coin-days they are able and willing to consume. ``Coin-days
-consumed'' is a measure of the product of the amount of coins spent, and the
-number of days the have not been previously spent. For example, to consume 10
+how many coin-days they are able and willing to consume. ``Coin-days consumed''
+is a measure of the product of the amount of coins spent in a transaction, and
+the number of days since they were last spent. For example, to consume 10
 coin-days, a currency holder can spend 10 Peercoin that they have held for a
@@
 To mint a new block, a minter creates a special transaction (presumably one
-where the minter pays themself) where one of the
-inputs has been unspent for at least 30 days. The resulting transaction, along
-with a timestamp, must meet a certain hash target that gets easier proportional to how many
-coin-days are consumed. For example, if the current difficulty gives a minter
-consuming 100 coin-days a 1\% chance of minting a block per second, a minter
-that was able to consume 200 coin-days would have a 2\% chance per second.
+where the minter pays themself) where one of the inputs has been unspent for at
+least 30 days. The resulting transaction, along with a timestamp, must meet a
+certain hash target that gets easier proportional to how many coin-days are
+consumed by the transaction. For example, if the current difficulty gives a
+minter consuming 100 coin-days a 1\% chance of minting a block per second, a
+minter that was able to consume 200 coin-days would have a 2\% chance per
+second.
 
@@
 transactions that the miner intends to include in this block, both as is done in
-Bitcoin. The miner then takes the SHA256 hash of the previous block header, the
-Merkle root of transactions (as generated in Bitcoin), and the secret nonce $N$,
-and hashes their concatenation using SHA256 to generate the
-32-byte \texttt{client\_random} the miner will use.
+Bitcoin. The miner then computes:
+\begin{equation}
+SHA256(prev\_block || merkle\_root || N)
+\end{equation}
+
+to generate the 32-byte \texttt{client\_random}, where $prev\_block$ is
+the SHA256 hash of the previous block header, $merkle\_root$ is the
+Merkle root of transactions (as computed in Bitcoin), and $N$ is the random nonce.
 
@@
 (such as the Diffie-Hellman parameters and the ephemeral public value generated
-by the server, or the curve parameters and a public curve point in ECDHE). These
-key exchange parameters, along with the \texttt{client\_random} and
-\texttt{server\_random},  are signed by the server using its private key; this
-signature can be verified by using the public key in the certificate.
+by the server, or the curve parameters and a public curve point in ECDHE). The
+server signs these key exchange parameters, along with the
+\texttt{client\_random} and \texttt{server\_random}. This signature can be
+verified with the public key in the certificate.
 
@@
 and \texttt{server\_random}, the signature value will be unpredictable to the
-client ahead of time. In other words, each signature will be a random value that
-depends on miner-provided value. Thus, it can be used as a proof-of-work in the
+client ahead of time. In addition, each signature will be a random value that
+depends on the miner-provided nonce. Thus, it can be used as a proof-of-work in the
 following way:
@@
 connection satisfies the proof-of-work threshold, and can be used to form the
-next block.
+next block. We hash $N$ a second time in this way to prevent the victim server
+from being able to tell if their response would satisfy the target difficulty.
+Otherwise, servers could simply withhold such responses, and no blocks could be
+published for them.
 
@@
 
-DDoSCoin is incompatible with earlier TLS (or even SSL) versions because the
-server key exchange signature does not include the \texttt{client\_random}, or
-any client-provided values. In earlier versions, the only value that provably comes from the server (i.e.
-is signed by a key tied to the victim's identity) does not contain any
-comittments from the client about the previous block, or what transactions
-should be included in the block. If we were to accept blocks where there was
-only a server signature that met some target difficulty, any miner could steal
-another miner's found block (and the contained block reward) by changing the
-transactions and forwarding the block.
+DDoSCoin is incompatible with versions of TLS before 1.2 (including SSL) because
+the server key exchange signature does not include the \texttt{client\_random}
+(or any client-provided values). In earlier versions, the only value that
+provably comes from the server (i.e.  is signed by a key tied to the victim's
+identity) does not contain any comittments from the client about the previous
+block, or what transactions should be included in the block. If we were to
+accept blocks where there was only a server signature that met some target
+difficulty, any miner could steal another miner's found block (and the contained
+block reward) by changing the transactions and forwarding the block.
 
@@
 
-This interesting property gives rise to an observation that with respect to
+As an aside, this interesting property gives rise to an observation that with respect to
 clients, the contents of TLS connections are \emph{deniable}. That is, it is not
@@
 particular server more complicated.  Nonetheless, identities in an SSH-based
-DDoSCoin could be based off of the server's host key, rather than a domain in a
+DDoSCoin could simply be the server's host key rather than a domain in a
 CA-signed certificate.
@@
 Although not yet implemented, the current TLS 1.3 proposal appears to also have the
-property of the server signing messages sent by the client. In particular, the
+necessary properties that enable DDoSCoin. In particular, the
 Certificate Verify message includes a signature from the server over essentially
@@
 create network connections, leading to the proof-of-work being a computational
-puzzle rather than one based on participation in a network denial of service.
-To prevent this, DDoSCoin must have a way to agree on what victims are
-acceptable targets for the proofs-of-work to be considered valid. Similarly, it
+puzzle rather than one based on participation in a denial of service over a
+network.
+To prevent this, DDoSCoin must have a way to agree on which victims are
+acceptable targets for the proofs-of-DDoS to be considered valid. Similarly, it
 is important to focus the denial-of-service effort toward a single or small
@@
 
-One simple solution is to hardcode a set of victim certificates into the
+One simple solution is to hardcode a set of victim identities into the
 protocol.  For example, DDoSCoin's published code could contain the identities
-of Facebook's servers and domains, and only allow and incentivize attacks
+(domain names)
+of Facebook's servers, and only allow and incentivize attacks
 against them. However, there are many attackers that might feel uncomfortable
-attacking Facebook, but would be willing to participate in attacks against other
+attacking Facebook, but are willing to participate in attacks against other
 websites. In addition, having only a single or small set of victim websites is a
 risk to DDoSCoin: if those websites all go offline or successfully mitigate the
-attacks (such as by disabling TLS), no future DDoSCoin blocks can be mined, and
-the currency will stall. At this point, all DDoSCoins in circulation would
+attacks, no future DDoSCoin blocks can be mined, and
+the currency will stall. If this happened, all DDoSCoins in circulation would
 become nearly worthless, as there would be no way to safely transact them.
@@
 
-To address these issues, we propose two mechanisms the DDoSCoin protocol can
-employ to allow victims to be selected by concensus.
+To address these issues, we propose two mechanisms that DDoSCoin can
+employ to allow victims to be selected by concensus. The first mechanism allows
+anyone to commit money to whoever can prove they sent an amount of traffic to a target
+(PAY\_TO\_DDOS). The second allows for updating the list of victim domains that
+miners are allowed to attack when mining for blocks.
 
@@
 create blocks, but with a few important differences. First, the
-\texttt{client\_random} is generated using the PAY\_TO\_DDOS transaction ID
-(txid), the SHA256 hash of the output script the payee wants to collect the
-payment with, and a random nonce.  The client then makes connections to the
+\texttt{client\_random} is generated as follows:
+\begin{equation}
+SHA256(txid || output\_script || N)
+\end{equation}
+
+where $txid$ is the transaction ID of the PAY\_TO\_DDOS transaction,
+$output\_script$ is the SHA256 hash of the output script the payee wants to collect the
+payment with, and $N$ is a 32-byte random nonce.  The client then makes connections to the
 specified victim domain until it gets a response that meets the target
 difficulty specified by the PAY\_TO\_DDOS transaction.
-(SHA256(\texttt{server\_key\_exchange\_params} || \texttt{signature} ||
-\texttt{nonce}) < target).
+($SHA256(server\_key\_exchange\_params || signature || N) < target$).
 
@@
 exchange signature. To validate the transaction, a miner must recompute the
-\texttt{client\_random} using the transaction ID of the PAY\_TO\_DDOS
-transaction, the hash of the output script in the claiming transaction, and the
-nonce. Then, the miner must verify that the certificate is valid for the
-provided domain (and rooted in a trusted CA), and that the certificate's
-signature over the server key exchange message is valid. Finally, the server
-must check that the server's response meets the target difficulty. If it does,
-then the transaction is valid and can be included in a block.
+\texttt{client\_random} as above. Then, the miner must verify that the
+certificate is valid for the provided domain (and rooted in a trusted CA), and
+that the certificate's signature over the server key exchange message is valid.
+Finally, the server must check that the server's response meets the target
+difficulty specified by the PAY\_TO\_DDOS transaction. If it does, then the
+transaction is valid and can be included in a block, letting the client collect
+the reward.
 
@@
 multiple bounty rewards with the same proof-of-DoS. Similarly, the client
-commits to (a hash of) the output script of the claiming transaction to
+commits to the output script of the claiming transaction to
 prevent others from being able to swap it for their own, therby ``stealing'' the
-proof-of-DoS and collect the reward themselves. These properties combined allow two
+proof-of-DoS and collecting the reward themselves. These properties combined allow two
 mutaully-distrusting parties to directly and safely transact currency in
@@
 After this block has been published, miners must wait until 10 proof-of-DoS
-(non-proof-of-stake) blocks have been mined before the specified delta to the
-change list is applied. This discourages malicious miners from forking the chain
-at an earlier block with a proof-of-stake block adding their local domain to the
-victim list, and immediately mining blocks on top of it to catch up to the main
-chain.
+(non-proof-of-stake) blocks have been mined with the old list of valid domains
+before the specified delta to the change list is applied. This discourages
+malicious miners from forking the chain at an earlier block with a
+proof-of-stake block adding their local domain to the victim list, and
+immediately mining blocks on top of it to catch up to the main chain.
 
@@
 We tested our proof-of-DDoS function (miner) against a quad-core server under
-our control, running nginx and connected to our attacker over a local Gigibit
-network. When running our miner, the CPU consumption of the server quickly
-reaches 100\% utilization on all 4 cores, while the attacker only requires
-approximately 30\% on a single core. This produces over 3000 TLS connections per
-second, and slowing responses to the server by more than a factor of 6 (see
-Figure~\ref{fig:eval}).
+our control, running nginx serving the default page and connected to our
+attacker over a local Gigibit Ethernet network. When running our miner, the CPU
+consumption of the server quickly reaches 100\% utilization on all 4 cores,
+while the attacker only requires approximately 30\% on a single core. This
+produces over 3000 TLS connections per second, and slows response times of the
+webserver considerably. We used Apache benchmark (ab) with 1000 connections with
+a concurrency of 50 to quantify this, and tested the server under normal
+conditions (no miner running) and under DoS (miner running). As shown in
+Figure~\ref{fig:eval}, we find that the average response time increases by more
+than a factor of 6.
 
@@
 
-There are several methods victim websites can use to defend themselves from
+Victim websites can use several methods to defend themselves from
 DDoSCoin miners. First, websites can simply disable TLS 1.2 entirely, and only
@@
 
-Alternatively, web servers can disable cipher modes that involve signatures from
+Alternatively, web servers can disable cipher modes that require signatures from
 the server. This would remove support for forward secure cipher suites, meaning
 that as long as the server's private key is accessible, any previously recorded
-TLS connections can be decrypted. We note that the current drafts of TLS 1.3
+TLS connections could be decrypted. We note that the current drafts of TLS 1.3
 propose to remove non-forward secure cipher suites entirely, possibly making it
@@
 
-Finally, websites could attempt to go after mining operations legally:
-Publishing a proof-of-DDoS block in the DDoSCoin blockchain may reveal intent to
-bring down a service for financial profit. If the victim webserver is able to
+Finally, websites could attempt to go after mining operations legally.
+Publishing a proof-of-DDoS block in the DDoSCoin blockchain may reveal the
+intent of a miner to attack a service for financial profit. If the victim webserver is able to
 log the traffic they receive, they can discover the IP address of the party
@@
 
-In this paper, we have presented a proof-of-DDoS, whereby cryptocurrency miners
-can prove their involvement in sending a large amount of requests to a specified
-victim webserver. Proof-of-DDoS can be used to replace proof-of-work in a
-cryptocurrency setting, provided that there is consensus around what victims are
-valid targets. Our conceptual alt-coin, DDoSCoin, provides such a concensus
-through two mechanisms: PAY\_TO\_DDOS, whereby a bounty can be set for DDoSing a
-given victim domain, and proof-of-stake updates to the list of valid victims.
+In this paper, we have presented a proof-of-DDoS cryptocurrency that allows
+miners to prove their involvement in sending a large amount of requests to a
+specified victim webserver. Proof-of-DDoS can be used to replace proof-of-work
+in a cryptocurrency setting, provided that there is consensus around what
+victims are valid targets. Our conceptual altcoin, DDoSCoin, provides such a
+concensus through two mechanisms: PAY\_TO\_DDOS, whereby a bounty can be set for
+DDoSing a given victim domain, and proof-of-stake updates to the list of valid
+victims.
 
-Cryptocurrency inovation continues to produce new and useful proof-of-work
+Cryptocurrency innovation continues to produce new and useful proof-of-work
 replacements. Still, proving access to arbitrary resources remains a difficult

### 2016-05-15 paper/paper.tex
spell cheque

@@
 hash-based computational puzzle employed by Bitcoin is instrumental to its
-security, preventing sybill attacks and making double-spending attacks more
+security, preventing Sybil attacks and making double-spending attacks more
 difficult. However, there have been concerns over the efficiency of this
@@
 In this paper, we present DDoSCoin, which is a cryptocurrency with a
-\emph{mallicious} proof-of-work. DDoSCoin allows miners to prove that they have
+\emph{malicious} proof-of-work. DDoSCoin allows miners to prove that they have
 contributed to a distributed denial of service attack against specific target
@@
 iterate over a large number of inputs to the hash function, and check if the
-output hash satisifes the partial preimage target. In simplified terms, to find
+output hash satisfies the partial preimage target. In simplified terms, to find
 an input that hashes to N bits of 0s, the miner must perform on average $2^{N}$
@@
 
-Many see this distributed computation as a collosal waste of CPU resources, and researchers have proposed
-alternative cryptocurrencies (altcoins) that aim to have more beneficial
-proofs-of-work~\cite{primecoin,permacoin} that provide utility beyond securing
-the underlying currency, such as finding chains of large primes or
-proving the archive of data. In this paper however, we investigate going in the
-opposite direction, and propose an altcoin that has a \emph{malicious}
-proof-of-work that is externally detrimental.
+Many see this distributed computation as a colossal waste of CPU resources, and
+researchers have proposed alternative cryptocurrencies (altcoins) that aim to
+have more beneficial proofs-of-work~\cite{primecoin,permacoin} that provide
+utility beyond securing the underlying currency, such as finding chains of
+large primes or proving the archive of data. In this paper however, we
+investigate going in the opposite direction, and propose an altcoin that has a
+\emph{malicious} proof-of-work that is externally detrimental.
 
@@
 we call \emph{DDoSCoin}. In addition to using proof-of-DDoS, DDoSCoin allows
-miners to select the victim servers by concensus using a proof-of-stake
+miners to select the victim servers by consensus using a proof-of-stake
 protocol. Rather than specify a single website or static list that DDoSCoin
-miners target, choosing them by concensus allows the choice of who is attacked
+miners target, choosing them by consensus allows the choice of who is attacked
 to be made collectively and fairly by DDoSCoin participants.
@@
 proof-of-work, with the intention of being ``ASIC-resistant'' in order to allow
-anyone to mine competatively with only a CPU~\cite{litecoin}.
+anyone to mine competitively with only a CPU~\cite{litecoin}.
 
@@
 resources solving a useless proof-of-work puzzle (as in Bitcoin), miners are
-instead incentivzed to store parts of a large agreed-upon file. In order to be
+instead incentivized to store parts of a large agreed-upon file. In order to be
 competitive in Permacoin, miners prove that they can retreive an assigned
@@
 semi-trusted centralized servers to assign Tor circuits to clients. It is also
-succeptible to collusion and sybil attacks by participants, however many of
+susceptible to collusion and sybil attacks by participants, however many of
 these attacks are outside the threat model of TorPath as it requires performing
@@
 block header that is less than an adjustable target. The block header includes
-the hash of the last block found, the merkle root of the list of transactions
+the hash of the last block found, the Merkle root of the list of transactions
 the miner wants to include in this block, and a nonce. The easiest way to solve
 this puzzle is to iterate the nonce\footnote{or modify transactions, therby
-changing the merkle root} until the hash satisfies the target difficulty. Then,
+changing the Merkle root} until the hash satisfies the target difficulty. Then,
 the miner publishes the found block, and miners use this block as the latest
@@
 hash is being compared to a target, here the only varying inputs are the
-long-lived (aged) input transaction, and a corse-grained timestamp with a
+long-lived (aged) input transaction, and a course-grained timestamp with a
 resolution of 1 second. Thus, for each aged unspent transaction output they
@@
 coin-holders from being able to disrupt the blockchain at a future date,
-potentially causing a large fork of the blockchain and destabalizing it.
+potentially causing a large fork of the blockchain and destabilizing it.
 
@@
 Miners in DDoSCoin repeatedly create connections to a TLS victim server, and
-check for a response that satisifes a target difficulty decided by the network.
-If the response satisifies this condition, then parameters of the TLS handshake
+check for a response that satisfies a target difficulty decided by the network.
+If the response satisfies this condition, then parameters of the TLS handshake
 can be published by the miner to create a new valid block.
@@
 
-To make a block, the miner publishes the prevoius block's hash, the transactions
+To make a block, the miner publishes the previous block's hash, the transactions
 (and their Merkle root), the nonce $N$, the \texttt{server\_random} value, the
@@
 certificate authority, and the domain name is in a list of acceptable victims.
-This list of valid victim domains is generated by concensus, and details for its
+This list of valid victim domains is generated by consensus, and details for its
 generation are discussed in Section~\ref{sec:victim}.
@@
 provably comes from the server (i.e.  is signed by a key tied to the victim's
-identity) does not contain any comittments from the client about the previous
+identity) does not contain any commitments from the client about the previous
 block, or what transactions should be included in the block. If we were to
@@
 Diffie-Hellman public value~\cite{rfc4253}. Either of these fields could be used
-to encode the necessary commitments (previous block, merkle root, and nonce)
+to encode the necessary commitments (previous block, Merkle root, and nonce)
 used in DDoSCoin.  However, SSH server identities are generally not signed by a
@@
 To address these issues, we propose two mechanisms that DDoSCoin can
-employ to allow victims to be selected by concensus. The first mechanism allows
+employ to allow victims to be selected by consensus. The first mechanism allows
 anyone to commit money to whoever can prove they sent an amount of traffic to a target
@@
 In order to allow victims to be (temporarily) selected for DoS, DDoSCoin allows
-``bounties'' for targetting specific servers. To accomplish this, DDoSCoin
+``bounties'' for targeting specific servers. To accomplish this, DDoSCoin
 introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in transactions
@@
 commits to the output script of the claiming transaction to
-prevent others from being able to swap it for their own, therby ``stealing'' the
+prevent others from being able to swap it for their own, thereby ``stealing'' the
 proof-of-DoS and collecting the reward themselves. These properties combined allow two
-mutaully-distrusting parties to directly and safely transact currency in
+mutually-distrusting parties to directly and safely transact currency in
 exchange for a specified-amount of work in a DoS attack.
@@
 have collected the payment. In addition, a potential victim website could
-disincentivze attacks by submitting PAY\_TO\_DDOS transactions that they can
+disincentivize attacks by submitting PAY\_TO\_DDOS transactions that they can
 quickly solve locally. This would cause attackers to try to connect to them, and
@@
 victims are valid targets. Our conceptual altcoin, DDoSCoin, provides such a
-concensus through two mechanisms: PAY\_TO\_DDOS, whereby a bounty can be set for
+consensus through two mechanisms: PAY\_TO\_DDOS, whereby a bounty can be set for
 DDoSing a given victim domain, and proof-of-stake updates to the list of valid
@@
 the use of bandwidth to a (potentially unwilling) target domain. We hope that
-this work encourages others to discover and inovate on novel proof-of-resource
+this work encourages others to discover and innovate on novel proof-of-resource
 puzzles.

### 2016-05-18 paper/paper.tex
Section on difficulty adjustment

@@
 
+\subsubsection{Difficulty Adjustment}
+
+The difficulty of proof-of-work changes dynamically in DDoSCoin, as it does in
+other crypto-currencies, in order to limit the rate at which new blocks are mined.
+However, in DDoSCoin, the difficulty is adjusted separately for each target domain. 
+The difficulty is not global, since domains could have different maximum throughputs, 
+allowing more or fewer connections from all miners over the same time period. Consider
+a single domain that handles many connections per second added to the target list. 
+The miners would connect to that server more often, since it will give more chances 
+at mining a block, and thus relieve traffic from the other targets.
+
+DDoSCoin adjusts diffuculty for a given domain as a function of the total number 
+of blocks mined, rather than the number of blocks mined by targetting that domain. 
+This allows target domains that somehow become more difficult to reach to quickly 
+return to a more appropriate difficulty, without having many blocks mined at the 
+high difficulty. This comes at a sacrifice to the agility of corrections when a 
+domain has too low of a difficulty. This allows a run on an easily mined domain 
+to occur for longer.
+
+We correct for this lower reactivity by dividing the number of blocks required 
+for a difficulty adjustment by the number of domains being targeted. Thus, as 
+more domains are in the target list and it becomes more likely that one may
+be able to handle many requests, the total number of mined blocks that will result
+in difficulty adjustment shrinks.
+
+A target's initial difficulty in DDoSCoin is decided by the stakeholder that
+introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
+set the difficulty too low, as the DDoS would be innefective. Also, many coins would be
+mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
+there will be a delay as other domains are mined, and the difficulty adjusts down
+to the appropriate level.
+
 %Proof-of-Stake to decide a delta on the victim-list.

### 2016-05-19 paper/paper.tex
edit pass through difficulty adjustment. am i understanding it correctly?

--- 2016-05-15 paper/paper.tex
@@
 
+\subsubsection{Difficulty Adjustment}
+
+The difficulty of proof-of-work changes dynamically in DDoSCoin, as it does in
+other crypto-currencies, in order to limit the rate at which new blocks are mined.
+However, in DDoSCoin, the difficulty is adjusted separately for each target domain. 
+Each victim domain has its own difficulty since domains could have different maximum throughputs, 
+allowing more or fewer connections from all miners over the same time period. Consider
+a single domain that handles many connections per second added to the target list. 
+The miners would connect to that server more often, since it will give more chances 
+at mining a block, and thus relieve traffic from the other targets.
+
+DDoSCoin adjusts diffuculty for a given domain by looking at the past
+BLOCK\_ADJUST blocks, and counting the number of blocks mined against
+the given domain. This ratio is compared to the expected ratio based on the
+current size of the victim list. If more blocks were mined than expected, the
+difficulty for this domain is increased. Similarly, if fewer blocks were mined,
+the difficulty for the domain is decreased.
+This mechanism allows target domains that somehow become more
+difficult to reach to quickly return to a more appropriate difficulty, without
+having to wait for many blocks mined at the high difficulty.
+
+At the same time, there is a global difficulty adjustment factor applied to all
+domain difficulties that is computed based only on the number of blocks mined
+over a given time. If blocks are being produced faster than expected, then the
+difficulty on all blocks increases. Likewise, blocks coming in slower than
+expected will reduce the global difficulty.
+
+%This comes at a
+%sacrifice to the agility of co when a domain has too low of a
+%difficulty. This allows a run on an easily mined domain to occur for longer.
+%
+
+%We correct for this lower reactivity by dividing the number of blocks required 
+%for a difficulty adjustment by the number of domains being targeted. Thus, as 
+%more domains are in the target list and it becomes more likely that one may
+%be able to handle many requests, the total number of mined blocks that will result
+%in difficulty adjustment shrinks.
+
+A target's initial difficulty in DDoSCoin is decided by the stakeholder that
+introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
+set the difficulty too low, as the DDoS would be innefective. Also, many coins would be
+mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
+there will be a delay as other domains are mined, and the difficulty adjusts down
+to the appropriate level.
+
 %Proof-of-Stake to decide a delta on the victim-list.

### 2016-05-20 paper/figures.tex
Added new figure

@@
     \label{fig:bitcoin-tx}
+\end{figure*}
+}
+
+\newcommand{\FigTLS}{
+\begin{figure*}[ht]
+    \centering
+    \includegraphics[width=0.9\textwidth,clip]{figures/tls.pdf}
+    \caption{\textbf{Miner--Target Interaction}\,--\, %
+	A single round-trip is required for each attempt to solve the proof-of-work. The client
+	computes the \texttt{client\_random} to commit to a given previous block and set of 
+	transactions, and only provides the server the option to use Diffie-Hellman Ephemeral
+	cipher-suites. The server then calculates a signature dependent on the 
+	\texttt{client\_random} and verifiable by the certificate the server provides.
+}
+    \label{fig:tls-connection}
 \end{figure*}

### 2016-05-20 paper/paper.tex
Added new figure
Adding in-text reference
Adding some text in PAY_TO_DDoS

@@
 \section{DDoSCoin Design}
+\FigTLS
 
@@
 If the response satisfies this condition, then parameters of the TLS handshake
-can be published by the miner to create a new valid block.
+can be published by the miner to create a new valid block. This connection is
+depicted in Figure~\ref{fig:tls-connection}.
 
@@
 Although not yet implemented, the current TLS 1.3 proposal appears to also have the
-necessary properties that enable DDoSCoin. In particular, the
+necessary properties that enable DDoSCoin~\cite{tls-draft}. In particular, the
 Certificate Verify message includes a signature from the server over essentially
@@
 specified victim domain until it gets a response that meets the target
-difficulty specified by the PAY\_TO\_DDOS transaction.
-($SHA256(server\_key\_exchange\_params || signature || N) < target$).
+difficulty specified by the PAY\_TO\_DDOS transaction, i.e. the hash of the key exchange 
+parameters, signature, and nonce are less than the target hash value.
 
@@
 % Maybe move this to discussion....
+
 Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
 the collector that by the time they complete their DoS attack, someone else will
-have collected the payment. In addition, a potential victim website could
+have collected the payment. Any target specified by a PAY\_TO\_DDOS transaction
+could use their priveleged position to turn the proof-of-work into a computational challenge.
+Since the challenge is no longer bound by the network, the target can claim the reward for
+themselves. Quickly solved PAY\_TO\_DDOS transactions with no degradation of service
+would indicate to the actor providing the bounty that the target is claiming its own bounty.
+
+In addition, a potential victim website could
 disincentivize attacks by submitting PAY\_TO\_DDOS transactions that they can

### 2016-05-20 paper/paper.tex
Discuss why the PAY_TO_DDoSer will pick a good difficulty

@@
 
+The bounty poster must select a difficulty that is appropriate for the target
+and reward. If the difficulty is too high, no miner will attack the target,
+because the miners do not want to waste effort. Also, if the difficulty is
+too low, the reward will be claimed for little degradation of service.
+
 To collect the bounty reward, the client creates an input script that will
@@
 there will be a delay as other domains are mined, and the difficulty adjusts down
-to the appropriate level.
+to the appropriate level. These are similar to the incentives for PAY\_TO\_DDOS 
+transactions, mentioned in Section~\ref{sec:pay-to-ddos}.
 

### 2016-05-20 paper/paper.tex
Adding outlines for Discussion

@@
 
-\if0
 \section{Discussion}
 
--Proof of (burnt) bandwidth
--Defenses
--Target server's participation
+%-Proof of (burnt) bandwidth
+%-Defenses
+%-Target server's participation
+
+Cryptocurrencies do good, from decentralizing money to finding primes. But they can do bad.
+
+What is being proved is bandwidth to a given endpoint.
+Unique challenge regarding priveleged position of owning target server.
+What does this means for active engagement as a potential target?
+
+Formalized reliance upon consensus for target-setting is weird
+
+Blockchain forking could enable miner rejection of a target, or rejection of target removal.
+This is true of PAY\_TO\_DDOS and adds risk of placing that transaction in your Merkle tree.
+
+Jumping the gun on PAY\_TO\_DDOS transactions before they find their way into the block chain
+could be weird. Especially if people start only inserting them as they solve the puzzle.
 
@@
 %\symbol{2544}
+- Proof-of-work
+
+- Attack websites we own
+
+- Did not publish the full coin
+
+- Bringing to light potential attacks
+
+- Having no alternative cipher suites in TLS 1.3 could be bad before a large committment
+
 \shrug
@@
 \subsection{Defenses}
-\fi
-\section{Defenses}
 
@@
 victim might be able to mine enough DDoSCoins to mint a proof-of-stake block
-that removes itself from the list.
+that removes itself from the list, or raise the difficulty of mining a block
+high enough that a remote miner has a negligable chance of suceeding.
 

### 2016-05-20 paper/paper.tex
Fleshing outlines of disc. and ethics

--- 2016-05-20 paper/paper.tex
@@
 
-\if0
 \section{Discussion}
 
--Proof of (burnt) bandwidth
--Defenses
--Target server's participation
+%-Proof of (burnt) bandwidth
+%-Defenses
+%-Target server's participation
+
+Bitcoin was invented with the goal of creating a decentralized digital currency, 
+and to that end has been more sucessful than most imagined. Banks are turning
+to ``Blockchain technology'' to solve issues regarding public ledgers.
+Primecoin and TorPath use cryptocurrencies to incentivize positive actions.
+However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
+malicousness inherent to the currency's design.
+
+DDoSCoin uses proof that the miner connected to a given server a sufficient number 
+of times as its proof-of-work. This is an indirect measurement of how much bandwidth
+to a given endpoint is being wasted by the miner. This provides a unique challenge
+when miners have different bandwidth to a given endpoint at a level beyond their direct 
+control. In prior cryptocurrencies, the proof-of-work uses resources entirely under the
+miner's control. The extreme of having a unique position to attack a site is being the
+target, and having the private key for the site. Having this priveleged position allows 
+the target to actively engage in DDoSCoin as a defense. We discuss this further in
+Section~\ref{sec:defense}.
+
+An interesting choice in the design of DDoSCoin is that the target-setting is done 
+dynamically, and by consensus. A given target can go offline, or in some other way
+defend against DDoSCoin at any point. When this happens, the currency cannot stall,
+as then no coins could be transacted. This necessitates dynamic target-setting, 
+despite how strange it may be to have the ``goalposts'' move on miners. This places
+risk in targetting sites that are likely to be removed from the target list, or
+\emph{controversial} sites. However, each site has its difficulty adjusted 
+individually, the controversial site will be easier to mine a block from as more 
+miners shy away, balancing the affect.
+
+While stakeholders have control of the target list, a majority of miners could
+use their choice of previous block to veto a given proof-of-stake block. This would
+be a fork of the blockchain. If a clear majority treat a block as malformed because
+it introduces an undesired domain, then the longer chain wins, and the undesired
+domain is not included in the target set, and any blocks mined on the chain with
+the vetoed target are not part of the blockchain.
+
+%Jumping the gun on PAY\_TO\_DDOS transactions before they find their way into the block chain
+%could be weird. Especially if people start only inserting them as they solve the puzzle.
+\todo{Talk about TLS 1.3, signing client controlled values}
 
@@
 %\symbol{2544}
+While we acknowlege this work introduces an idea that could be used to incentivize 
+malicous behavior, the ethics of this paper are controlled. We only demonstrate a 
+proof of concept, and in doing so, only attack websites we have ownership of.
+Further, we do not publish the full coin, and keep the source of our proof of concept
+closed. We believe it important to fully disclose potential attacks, even those that
+require the development of an altcoin to execute. This is especially important in the
+face of the impending commitment to the design of TLS 1.3, and compounded by how long 
+TLS/SSL protocol versions stay in active use.
+
 \shrug
@@
 \subsection{Defenses}
-\fi
-\section{Defenses}
+\label{sec:defense}
 

### 2016-05-20 paper/paper.tex
Adding a little clarification

@@
 
+Many positive results have come from cryptocurrencies.
 Bitcoin was invented with the goal of creating a decentralized digital currency, 
@@
 However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
-malicousness inherent to the currency's design.
+malicousness inherent to a currency's design, turning the notion of what constitutes
+a ``useful'' proof-of-work on its head. Certainly a DDoS attack it useful to someone,
+but negatively impacts society as a whole.
 
@@
 to a given endpoint is being wasted by the miner. This provides a unique challenge
-when miners have different bandwidth to a given endpoint at a level beyond their direct 
-control. In prior cryptocurrencies, the proof-of-work uses resources entirely under the
-miner's control. The extreme of having a unique position to attack a site is being the
-target, and having the private key for the site. Having this priveleged position allows 
+when miners have different bandwidths to that given endpoint. The extreme of 
+having a different bandwidth is being the target, and having the private key 
+for the site. Having this priveleged position allows 
 the target to actively engage in DDoSCoin as a defense. We discuss this further in
@@
 TLS/SSL protocol versions stay in active use.
-
-\shrug
 

### 2016-05-20 paper/paper.tex
Fixes

@@
 
-An interesting choice in the design of DDoSCoin is that the target-setting is done 
+An interesting choice in the design of DDoSCoin is target-setting is done 
 dynamically, and by consensus. A given target can go offline, or in some other way
@@
 domain is not included in the target set, and any blocks mined on the chain with
-the vetoed target are not part of the blockchain.
+the vetoed target are not part of the blockchain. This allows the miners to coordinate
+and self-enforce a blacklist, or whitelist, of target domains, so long as they 
+have sufficient participation in the policy.
 

### 2016-05-20 paper/paper.tex
Moving TLS 1.3 to discussion
Ethics changes

@@
 
-Although not yet implemented, the current TLS 1.3 proposal appears to also have the
-necessary properties that enable DDoSCoin~\cite{tls-draft}. In particular, the
-Certificate Verify message includes a signature from the server over essentially
-all prior handshake messages, including the Client Hello that contains the
-\texttt{client\_random}. Thus, DDoSCoin could be used against TLS 1.3
-servers with only minor modifications.
-
 \subsection{Victim Selection}
@@
 %could be weird. Especially if people start only inserting them as they solve the puzzle.
-\todo{Talk about TLS 1.3, signing client controlled values}
+
+Although not yet implemented, the current TLS 1.3 proposal appears to also have the
+necessary properties that enable DDoSCoin~\cite{tls-draft}. In particular, the
+Certificate Verify message includes a signature from the server over essentially
+all prior handshake messages, including the Client Hello that contains the
+\texttt{client\_random}. Thus, DDoSCoin could be used against TLS 1.3
+servers with only minor modifications. This should be considered in the design of 
+TLS 1.3 due to the long life of TLS implementations.
 
@@
 proof of concept, and in doing so, only attack websites we have ownership of.
-Further, we do not publish the full coin, and keep the source of our proof of concept
+Further, we do not publish the full coin, and keep the source of our proof-of-concept
 closed. We believe it important to fully disclose potential attacks, even those that
@@
 face of the impending commitment to the design of TLS 1.3, and compounded by how long 
-TLS/SSL protocol versions stay in active use.
+TLS/SSL protocol versions stay in active use. Further, proof-of-DDoS has applications 
+beyond just DDoSCoin.
 

### 2016-05-24 paper/paper.tex
Open source software!
Revision pass

@@
 servers.  This proof involves making a large number of TLS connections to a
-target server, and using infrequent cryptographic responses to prove that a
+target server, and using cryptographic responses to prove that a
 large number of connections has been made. Like proof-of-work puzzles, these
@@
 
-Cryptocurrencies rely on proofs-of-work (PoW) that require miners to spend a
+Cryptocurrencies rely on proofs-of-work that require miners to spend a
 large amount of effort to solve a specific puzzle.  Solutions to these puzzles,
@@
 Many see this distributed computation as a colossal waste of CPU resources, and
-researchers have proposed alternative cryptocurrencies (altcoins) that aim to
+researchers have proposed alternative cryptocurrencies, or altcoins, that aim to
 have more beneficial proofs-of-work~\cite{primecoin,permacoin} that provide
-utility beyond securing the underlying currency, such as finding chains of
+utility beyond securing the underlying currency: finding chains of
 large primes or proving the archive of data. In this paper however, we
@@
 In particular, we propose a proof-of-work that allows miners to prove they have
-participated in a distributed denial of service (DDoS) attack against a
+participated in a distributed denial of service, or DDoS, attack against a
 particular target. Miners are incentivized to send and receive large amounts of network
-traffic at the target in order to produce a valid proof-of-work. As in other
+traffic to and from the target in order to produce a valid proof-of-work. As in other
 cryptocurrencies, these proofs can be inexpensively verified by others, and the
 original miner can collect a reward. This reward can be sold for other
-currencies (including Bitcoin or even traditional currencies), allowing botnet
+currencies, including Bitcoin or even traditional currencies, allowing botnet
 owners and other attacks to directly collect revenue for their assistance
@@
 returned by the server is not predictable to the client, and is randomly
-distributed. Thus, clients can use a similar trick as in Bitcoin, and only
+distributed. Thus, clients can use a similar trick to those in Bitcoin, and only
 report connections that match some rare threshold, such as the signature from
@@
 \item Propose a novel conceptual cryptocurrency, DDoSCoin, whose proof-of-work
-incentives miners to participate in a DDoS attack, and allows them prove they have done so.
+incentives miners to participate in a DDoS attack, and allows them prove they have done so
 \item Describe a way for target victims to be chosen by consensus of its
-participants.
+participants
 \item Implement our proof-of-work function and evaluate its performance and
-impact.
+impact
 \item Discuss several defenses against such a cryptocurrency that potential
-victims can employ.
+victims can employ
 \end{itemize}
@@
 
-Many alternate cryptocurrency protocols (altcoins) have been proposed since the
+Many alternate cryptocurrency protocols have been proposed since the
 creation of Bitcoin. Although none have yet eclipsed the popularity of Bitcoin,
@@
 \emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
-resources solving a useless proof-of-work puzzle (as in Bitcoin), miners are
+resources solving a useless proof-of-work puzzle, such as in Bitcoin, miners are
 instead incentivized to store parts of a large agreed-upon file. In order to be
@@
 susceptible to collusion and sybil attacks by participants, however many of
-these attacks are outside the threat model of TorPath as it requires performing
+these attacks are outside the threat model of TorPath, as it requires performing
 those attacks against the underlying Tor network. In contrast, DDoSCoin does not
@@
 limited~\cite{bitcoin-paper}. Ethereum allows transactions to be
-\emph{programmable contracts}, whereby a programmer can specify in a custom
-scripting language arbitrary logic, including conditional payments or
-fee-collection. While the Ethereum Virtual Machine (EVM) that executes these
+\emph{programmable contracts}, whereby a transaction can be specified in a custom
+scripting language with arbitrary logic, including conditional payments or
+fee-collection. While the Ethereum Virtual Machine that executes these
 contracts does not provide external network access to the scripts, it could
@@
 computational puzzle in order to mine blocks. Mining a block nets the miner a
-reward, and the right to specify what new (valid) transactions should be
+reward and the right to specify what new, valid transactions should be
 included in the public ledger. To mine a block, a miner must find a hash of a
@@
 block to be considered valid. Transactions in Bitcoin are scripts, and each new
-transactions specifies an \emph{output script} that must be satisfied in order
+transaction specifies an \emph{output script} that must be satisfied in order
 for the coins
@@
 provides an input (scriptSig) that ``solves'' the previous transactions' output
-(scriptPubKey); in this case, a valid signature over the new transaction. This
+(scriptPubKey). In this case, a valid signature over the new transaction. This
 new transaction can then specify a new output (scriptPubKey) for these coins.
@@
 day, or equivalently, spend 5 Peercoins that were last spent 2 days ago. Note
-that the holder can send these coins to anyone (including themselves) in order
+that the holder can send these coins to anyone, including themselves, in order
 to consume the coin age.
 
-To mint a new block, a minter creates a special transaction (presumably one
-where the minter pays themself) where one of the inputs has been unspent for at
+To mint a new block, a minter creates a special transaction, presumably one
+where the minter pays themself, where one of the inputs has been unspent for at
 least 30 days. The resulting transaction, along with a timestamp, must meet a
@@
 hash is being compared to a target, here the only varying inputs are the
-long-lived (aged) input transaction, and a course-grained timestamp with a
+long-lived input transaction, and a course-grained timestamp with a
 resolution of 1 second. Thus, for each aged unspent transaction output they
@@
 the SHA256 hash of the previous block header, $merkle\_root$ is the
-Merkle root of transactions (as computed in Bitcoin), and $N$ is the random nonce.
+Merkle root of transactions as computed in Bitcoin, and $N$ is the random nonce.
 
@@
 Next, the server sends its certificate chain, and a server key exchange message.
-The certificate chain contains the server's (signed) TLS certificate, as well as
-intermediate certificate authorities (CAs) that create a signature chain to a
+The certificate chain contains the server's signed TLS certificate, as well as
+intermediate certificate authorities that create a signature chain to a
 browser-trusted root CA. Inside the server's certificate is a public
-key, as well as the identity of the server (i.e. it's domain). The miner stores
+key, as well as the identity of the server represented by it's domain. The miner stores
 these for verification in case a block is found.
@@
 In the server key exchange message, the server sends key exchange parameters
-(such as the Diffie-Hellman parameters and the ephemeral public value generated
-by the server, or the curve parameters and a public curve point in ECDHE). The
+such as the Diffie-Hellman parameters and the ephemeral public value generated
+by the server, or the curve parameters and a public curve point in ECDHE. The
 server signs these key exchange parameters, along with the
@@
 
-Because the server key exchange signature contains the \texttt{client\_random}
+Since the server key exchange signature contains the \texttt{client\_random}
 and \texttt{server\_random}, the signature value will be unpredictable to the
 client ahead of time. In addition, each signature will be a random value that
-depends on the miner-provided nonce. Thus, it can be used as a proof-of-work in the
-following way:
+depends on the miner-provided nonce. Thus, it can be used as a proof-of-work.
 
@@
 clients, the contents of TLS connections are \emph{deniable}. That is, it is not
-possible for a client to record a TLS connection (including its chosen secrets)
+possible for a client to record a TLS connection, including its chosen secrets,
 and report this to a third party in a way that cryptographically proves what the
@@
 
-Besides TLS 1.2, there are other cryptographic protocols that include the server
+Besides TLS 1.2, there are other cryptographic protocols that involve the server
 signing a client-chosen value. For example, the SSH protocol key exchange
@@
 trusted party, making verification that a miner has communicated with a
-particular server more complicated.  Nonetheless, identities in an SSH-based
+particular server more challenging.  Nonetheless, identities in an SSH-based
 DDoSCoin could simply be the server's host key rather than a domain in a
@@
 access to the private key for that server, they would not be required to even
-create network connections, leading to the proof-of-work being a computational
+create network connections, reducing the proof-of-work to a computational
 puzzle rather than one based on participation in a denial of service over a
@@
 acceptable targets for the proofs-of-DDoS to be considered valid. Similarly, it
-is important to focus the denial-of-service effort toward a single or small
+is important to focus the denial-of-service effort toward a small
 number of victims in order to have the most impact.
@@
 employ to allow victims to be selected by consensus. The first mechanism allows
-anyone to commit money to whoever can prove they sent an amount of traffic to a target
+anyone to commit DDoSCoins to whoever can prove they sent an amount of traffic to a target
 (PAY\_TO\_DDOS). The second allows for updating the list of victim domains that
@@
 server and obtaining a response that meets the given target difficulty. These
-connections are made similar to the way that miners connect to victim servers to
+connections are made similar to how miners connect to victim servers to
 create blocks, but with a few important differences. First, the
@@
 themselves. Quickly solved PAY\_TO\_DDOS transactions with no degradation of service
-would indicate to the actor providing the bounty that the target is claiming its own bounty.
+and sufficiently difficult proof-of-work
+would indicate to the bounty provider that the target is claiming its bounty.
 
@@
 done by actors that already have a substantial stake in the currency, either by
-purchasing it or by previously participating in the (DoS) mining themselves.
+purchasing it or by previously participating in the mining themselves.
 
@@
 hashes the aged transaction, a recent stake-modifier block, and a current
-(seconds-resolution) timestamp. If this hash is less than the current
+seconds-resolution timestamp. If this hash is less than the current
 proof-of-stake target difficulty multiplied by the coin-age being consumed in
@@
 proof-of-stake block. Inside this block, the currency holder can make one
-addition to (or one deletion from) the current victim list.
+addition to or one deletion from the current victim list.
 
@@
 After this block has been published, miners must wait until 10 proof-of-DoS
-(non-proof-of-stake) blocks have been mined with the old list of valid domains
+blocks have been mined with the old list of valid domains
 before the specified delta to the change list is applied. This discourages
@@
 malicousness inherent to a currency's design, turning the notion of what constitutes
-a ``useful'' proof-of-work on its head. Certainly a DDoS attack it useful to someone,
+a ``useful'' proof-of-work around. Certainly a DDoS attack it useful to someone,
 but negatively impacts society as a whole.
@@
 to a given endpoint is being wasted by the miner. This provides a unique challenge
+to the currency 
 when miners have different bandwidths to that given endpoint. The extreme of 
@@
 defend against DDoSCoin at any point. When this happens, the currency cannot stall,
-as then no coins could be transacted. This necessitates dynamic target-setting, 
-despite how strange it may be to have the ``goalposts'' move on miners. This places
-risk in targetting sites that are likely to be removed from the target list, or
-\emph{controversial} sites. However, each site has its difficulty adjusted 
-individually, the controversial site will be easier to mine a block from as more 
-miners shy away, balancing the affect.
+as then no coins could be transacted. This necessitates dynamic target-setting.
 
@@
 proof of concept, and in doing so, only attack websites we have ownership of.
-Further, we do not publish the full coin, and keep the source of our proof-of-concept
-closed. We believe it important to fully disclose potential attacks, even those that
+Further, we do not publish the full coin.
+We believe it important to fully disclose potential attacks, even those that
 require the development of an altcoin to execute. This is especially important in the

### 2016-05-25 paper/figures.tex
Formatting

@@
     \includegraphics[width=0.9\textwidth,trim={0 6.5cm 1cm 0},clip]{btc-transaction.pdf}
-    \caption{\textbf{Standard Bitcoin transaction script}\,--\, %
+    \caption{\textbf{Standard Bitcoin transaction script}\,---\, %
             Transaction \#10 spends \#9 by providing a
@@
     \includegraphics[width=0.9\textwidth,clip]{figures/tls.pdf}
-    \caption{\textbf{Miner--Target Interaction}\,--\, %
+    \caption{\textbf{Miner--Target Interaction}\,---\, %
 	A single round-trip is required for each attempt to solve the proof-of-work. The client
@@
     \includegraphics[width=0.9\textwidth,trim={0 9.5cm 9.2cm 0},clip]{ddoscoin-overview.pdf}
-    \caption{\textbf{DDoSCoin Design}\,--\, %
+    \caption{\textbf{DDoSCoin Design}\,---\, %
     DDoSCoin miners make repeated connections to a victim server running TLSv1.2
@@
     \includegraphics[width=0.9\linewidth]{../data/times.pdf}
-    \caption{\textbf{DDoSCoin effect}\,--\, %
+    \caption{\textbf{DDoSCoin effect}\,---\, %
     We set up a quad-core nginx HTTPS server on a local network, and used Apache

### 2016-05-25 paper/paper.tex
Formatting

@@
 
-\emph{Contributions}
+\noindent\textbf{Contributions:}
 \begin{itemize}
@@
 intermediate certificate authorities that create a signature chain to a
-browser-trusted root CA. Inside the server's certificate is a public
+browser-trusted root CA\@. Inside the server's certificate is a public
 key, as well as the identity of the server represented by it's domain. The miner stores
@@
 such as the Diffie-Hellman parameters and the ephemeral public value generated
-by the server, or the curve parameters and a public curve point in ECDHE. The
+by the server, or the curve parameters and a public curve point in ECDHE\@. The
 server signs these key exchange parameters, along with the
@@
 the \texttt{client\_random} is to prevent a client from ``double-claiming''
-multiple bounty rewards with the same proof-of-DoS. Similarly, the client
+multiple bounty rewards with the same proof-of-DoS\@. Similarly, the client
 commits to the output script of the claiming transaction to
@@
 To evaluate the performance and effectiveness of DDoSCoin, we implement our
-proof-of-DDoS function in 582 lines of C. Our mining code uses
+proof-of-DDoS function in 582 lines of C\@. Our mining code uses
 libevent~\cite{libevent} and OpenSSL~\cite{openssl} to create concurrent

### 2016-05-25 paper/paper.tex
minor edits until earlier tls

@@
 output hash satisfies the partial preimage target. In simplified terms, to find
-an input that hashes to N bits of 0s, the miner must perform on average $2^{N}$
+an input that hashes to N bits of zeros, the miner must perform on average $2^{N}$
 hashes. Once such an input is found, other miners and Bitcoin nodes can verify the
@@
 as a proof of connection. In modern versions of TLS, the server signs a
-client-provided parameter of the connection, along with server-provided values
+client-provided parameter during the handshake, along with server-provided values
 used in the key exchange of the connection. This allows the client to prove to
@@
 returned by the server is not predictable to the client, and is randomly
-distributed. Thus, clients can use a similar trick to those in Bitcoin, and only
+distributed. Thus, clients can use a similar trick as in Bitcoin, and only
 report connections that match some rare threshold, such as the signature from
-the server starts with $N$ bits of 0s. On average, it will take clients $2^{N}$
+the server starts with $N$ bits of zeros. On average, it will take clients $2^{N}$
 connections to produce such a proof.
@@
 creation of Bitcoin. Although none have yet eclipsed the popularity of Bitcoin,
-many altcoins have interesting innovations, often in the form of alternate
+many so-called altcoins have interesting innovations, often in the form of alternate
 proof-of-work. For example, Litecoin uses scrypt in place of SHA256 in its
@@
 numbers~\cite{primecoin}. Although Primecoin has found several large Cunningham
-and bi-twin chains, it remains unclear if such primes have any practical use.
+and bi-twin prime chains, it remains unclear if such primes have any practical use.
 
@@
 semi-trusted centralized servers to assign Tor circuits to clients. It is also
-susceptible to collusion and sybil attacks by participants, however many of
+susceptible to collusion and Sybil attacks by participants, however many of
 these attacks are outside the threat model of TorPath, as it requires performing
@@
 require any centralized parties for the proof-of-DDoS, besides trusting existing
-certificate authorities to validate domains.
+TLS certificate authorities to validate domains.
 
@@
 proof-of-DDoS for a specified target. This would effectively accomplish the same
-outcome as PAY\_TO\_DDOS (described in Section~\ref{sec:pay-to-ddos}), and
+outcome as PAY\_TO\_DDOS (described in Section~\ref{sec:pay-to-ddos}) by
 implementing DDoSCoin's proof-of-DDoS verification.
@@
 
-Each block commits to a set of transactions, which each must be valid for the
+Each block commits to a set of transactions, where each must be valid for the
 block to be considered valid. Transactions in Bitcoin are scripts, and each new
@@
 
-When a proof-of-stake is minted, the minter is allowed to collect a small
+When a proof-of-stake block is minted, the minter is allowed to collect a small
 subsidy proportional to the coin-age consumed in their proof-of-stake

### 2016-05-25 paper/paper.tex
spell check

@@
 instead incentivized to store parts of a large agreed-upon file. In order to be
-competitive in Permacoin, miners prove that they can retreive an assigned
+competitive in Permacoin, miners prove that they can retrieve an assigned
 portion of the file.
@@
 the miner wants to include in this block, and a nonce. The easiest way to solve
-this puzzle is to iterate the nonce\footnote{or modify transactions, therby
+this puzzle is to iterate the nonce\footnote{or modify transactions, thereby
 changing the Merkle root} until the hash satisfies the target difficulty. Then,
@@
 
-where $txid$ is the transaction ID of the PAY\_TO\_DDOS transaction,
+Where $txid$ is the transaction ID of the PAY\_TO\_DDOS transaction,
 $output\_script$ is the SHA256 hash of the output script the payee wants to collect the
@@
 have collected the payment. Any target specified by a PAY\_TO\_DDOS transaction
-could use their priveleged position to turn the proof-of-work into a computational challenge.
+could use their privileged position to turn the proof-of-work into a computational challenge.
 Since the challenge is no longer bound by the network, the target can claim the reward for
@@
 
-DDoSCoin adjusts diffuculty for a given domain by looking at the past
+DDoSCoin adjusts difficulty for a given domain by looking at the past
 BLOCK\_ADJUST blocks, and counting the number of blocks mined against
@@
 introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
-set the difficulty too low, as the DDoS would be innefective. Also, many coins would be
+set the difficulty too low, as the DDoS would be ineffective. Also, many coins would be
 mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
@@
 However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
-malicousness inherent to a currency's design, turning the notion of what constitutes
+maliciousness inherent to a currency's design, turning the notion of what constitutes
 a ``useful'' proof-of-work around. Certainly a DDoS attack it useful to someone,
@@
 having a different bandwidth is being the target, and having the private key 
-for the site. Having this priveleged position allows 
+for the site. Having this privileged position allows 
 the target to actively engage in DDoSCoin as a defense. We discuss this further in
@@
 %\symbol{2544}
-While we acknowlege this work introduces an idea that could be used to incentivize 
-malicous behavior, the ethics of this paper are controlled. We only demonstrate a 
+While we acknowledge this work introduces an idea that could be used to incentivize 
+malicious behavior, the ethics of this paper are controlled. We only demonstrate a 
 proof of concept, and in doing so, only attack websites we have ownership of.
@@
 that removes itself from the list, or raise the difficulty of mining a block
-high enough that a remote miner has a negligable chance of suceeding.
+high enough that a remote miner has a negligible chance of succeeding.
 

### 2016-05-25 paper/paper.tex
discussion section and defenses update

@@
 
-DDoSCoin adjusts difficulty for a given domain by looking at the past
+DDoSCoin adjusts difficulty for a given domain by looking at the previous
 BLOCK\_ADJUST blocks, and counting the number of blocks mined against
 the given domain. This ratio is compared to the expected ratio based on the
-current size of the victim list. If more blocks were mined than expected, the
+current size of the victim list and the time over which these blocks were mined
+(based on a timestamp included in the blocks). If more blocks were mined than
+expected, the
 difficulty for this domain is increased. Similarly, if fewer blocks were mined,
@@
 having to wait for many blocks mined at the high difficulty.
-
-At the same time, there is a global difficulty adjustment factor applied to all
-domain difficulties that is computed based only on the number of blocks mined
-over a given time. If blocks are being produced faster than expected, then the
-difficulty on all blocks increases. Likewise, blocks coming in slower than
-expected will reduce the global difficulty.
 
@@
 introduces the target in a proof-of-stake block. The stakeholder is incentivized to not
-set the difficulty too low, as the DDoS would be ineffective. Also, many coins would be
+set the difficulty too low, as many coins would be
 mined quickly, devaluing the stakeholder's own coins. If the difficulty is set too high,
 there will be a delay as other domains are mined, and the difficulty adjusts down
-to the appropriate level. These are similar to the incentives for PAY\_TO\_DDOS 
-transactions, mentioned in Section~\ref{sec:pay-to-ddos}.
+to the appropriate level.
+%These are similar to the incentives for PAY\_TO\_DDOS 
+%transactions, mentioned in Section~\ref{sec:pay-to-ddos}.
 
@@
 libevent~\cite{libevent} and OpenSSL~\cite{openssl} to create concurrent
-connections toward a specific target, testing each response to see if it
+connections toward a specific target, crafting a
+\texttt{client\_random} in the specified way and testing each response to see if it
 satisfies a hard-coded proof-of-DDoS target difficulty.
 
-We tested our proof-of-DDoS function (miner) against a quad-core server under
+We tested our proof-of-DDoS function (miner) against a quad-core TLS server under
 our control, running nginx serving the default page and connected to our
@@
 conditions (no miner running) and under DoS (miner running). As shown in
-Figure~\ref{fig:eval}, we find that the average response time increases by more
-than a factor of 6.
+Figure~\ref{fig:eval}, we find that the average server response time increases by more
+than a factor of 6 when our miner is running.
 
@@
 maliciousness inherent to a currency's design, turning the notion of what constitutes
-a ``useful'' proof-of-work around. Certainly a DDoS attack it useful to someone,
-but negatively impacts society as a whole.
+a ``useful'' proof-of-work around.
 
-DDoSCoin uses proof that the miner connected to a given server a sufficient number 
-of times as its proof-of-work. This is an indirect measurement of how much bandwidth
-to a given endpoint is being wasted by the miner. This provides a unique challenge
-to the currency 
-when miners have different bandwidths to that given endpoint. The extreme of 
-having a different bandwidth is being the target, and having the private key 
-for the site. Having this privileged position allows 
-the target to actively engage in DDoSCoin as a defense. We discuss this further in
-Section~\ref{sec:defense}.
+DDoSCoin uses a proof that the miner has connected to a given server a sufficient number 
+of times as its proof-of-work. This is an indirect measurement of how much
+bandwidth or resources are being spent by the victim. Although miners only
+receive DDoSCoins in return for this effort, these can be traded in for other
+currency via cryptocurrency exchanges. In addition, because DDoSCoin uses
+transactions similar to Bitcoin, trust-less cross-chain transactions can allow
+DDoSCoins to be traded for Bitcoins without requiring a trusted 3rd party
+intermediary. Thus, even outlawing DDoSCoins from exchanges does not prevent a
+black-market from getting around these sanctions.
 
@@
 While we acknowledge this work introduces an idea that could be used to incentivize 
-malicious behavior, the ethics of this paper are controlled. We only demonstrate a 
-proof of concept, and in doing so, only attack websites we have ownership of.
-Further, we do not publish the full coin.
+malicious behavior, we have taken precautions to limit harm. First, in
+demonstrating our proof-of-concept and evaluating our proof-of-DDoS code, we
+have only ``attacked'' websites we have ownership and authority over.
+Further, we are not publishing a working alt-coin that uses this proof-of-DDoS,
+but rather a conceptual description of one.
 We believe it important to fully disclose potential attacks, even those that
@@
 face of the impending commitment to the design of TLS 1.3, and compounded by how long
-TLS/SSL protocol versions stay in active use. Further, proof-of-DDoS has applications 
-beyond just DDoSCoin.
+TLS/SSL protocol versions stay in active use.
+
+%Further, proof-of-DDoS has applications 
+%beyond just DDoSCoin.
 
@@
 more difficult to defend against DDoSCoin in TLS 1.3.
+
+Although dramatically changing existing deployed versions of TLS is unrealistic, it may still
+be possible to influence the design of the TLS 1.3 standard to make it
+incompatible with DDoSCoin. For example, rather than having the server sign all
+of the handshake messages (including those from the client), the server could
+sign only the handshake messages which it sent. This may not fully mitigate
+DDoSCoin, as some of the parameters (such as the selected cipher suite or
+elliptic curves) may have originally been provided by the client. We note that
+while the server signing only its own messages still mitigates many previous
+known bugs such as those revealed in the FREAK TLS attack, there may be other subtle bugs that are
+exposed by servers not signing client's messages.
 

### 2016-05-26 paper/fixup.py
i know where i work

@@ -1,0 +1,43 @@
+#!/usr/bin/python
+
+import sys
+import hashlib
+import time
+
+
+f = open(sys.argv[1], 'rb')
+data = f.read()
+f.close()
+
+CREATION_STR = 'CreationDate (D:'
+MOD_STR = 'ModDate (D:'
+c_index = data.index(CREATION_STR) + len(CREATION_STR)
+m_index = data.index(MOD_STR) + len(MOD_STR)
+
+c_index_end = c_index + 14  # 20160401001122
+m_index_end = m_index + 14
+
+if (m_index < c_index):
+    print 'Weird order of indexes...aborting'
+    sys.exit(1)
+
+t = int(time.time())
+n = 0
+while True:
+    t += 1
+    n += 1
+
+    date_str = time.strftime('%Y%m%d%H%M%S', time.localtime(t))
+    new_data = data[0:c_index] + date_str + \
+                data[c_index_end:m_index] + \
+                date_str + \
+                data[m_index_end:]
+
+    h = hashlib.sha1(new_data).hexdigest()
+    print t, h
+    if h[0:3] == '666':
+        print 'Found after %d iterations, %s' % (n, time.strftime('%Y-%m-%d-%H:%M:%S', time.localtime(t)))
+        f = open(sys.argv[1], 'wb')
+        f.write(new_data)
+        f.close()
+        sys.exit(0)

### 2016-05-26 paper/fixup-id.c
add c version, goes fast

@@ -1,0 +1,105 @@
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <openssl/sha.h>
+#include <stdint.h>
+#define _GNU_SOURCE
+#include <string.h>
+
+// Increment a 32-nibble hex number at offset
+void increment(uint8_t *data, size_t offset)
+{
+    offset += 31;
+
+    while (1) {
+        data[offset]++;
+
+
+        if (data[offset] > '9' && data[offset] < 'A') {
+            data[offset] = 'A';
+        }
+
+        if (data[offset] > 'F') {
+            data[offset] = '0';
+            offset--;
+        } else {
+            break;
+        }
+    }
+}
+
+// For some reason, memmem doesn't want to work on my system :(
+// So I implement a naive version here.
+void *my_memmem(void *haystack, size_t haystack_len, void *needle, size_t needle_len)
+{
+    size_t i = 0;
+    uint8_t *p = haystack;
+    while (i < haystack_len - needle_len) {
+        if (memcmp(p++, needle, needle_len) == 0) {
+            return (p - 1);
+        }
+        i++;
+    }
+    return NULL;
+}
+
+int main(int argc, char *argv[])
+{
+    uint8_t *data;
+
+    FILE *f = fopen(argv[1], "r");
+    fseek(f, 0L, SEEK_END);
+    size_t sz = ftell(f);
+    data = malloc(sz);
+    rewind(f);
+    fread(data, sz, 1, f);
+    fclose(f);
+    printf("Read %zu bytes\n", sz);
+
+
+    // Find "/ID [<"
+    char *str = "/ID [<";
+    uint8_t *offset = my_memmem(data, sz, str, strlen(str));
+    printf("data: %p, str: %p, offset: %p\n", data, str, offset);
+    uint8_t *offset2 = my_memmem(offset, sz - (offset - data), ">]", 2);
+
+
+    size_t offset_n1 = (offset - data) + 6;
+    size_t offset_n2 = offset_n1 + 35;
+
+    printf("offset 1: %zu, offset 2: %zu\n", offset_n1, offset_n2);
+    uint8_t md[SHA_DIGEST_LENGTH];
+
+    uint8_t min_md[SHA_DIGEST_LENGTH];
+    SHA1(data, sz, min_md);
+    size_t i = 0;
+
+    int j;
+    for (j=0; j<SHA_DIGEST_LENGTH; j++) {
+        printf("%02x", min_md[j]);
+    }
[…]

### 2016-07-21 paper/paper.tex
minor typos, +acknowledgements section

@@
 \item Propose a novel conceptual cryptocurrency, DDoSCoin, whose proof-of-work
-incentives miners to participate in a DDoS attack, and allows them prove they have done so
+incentives miners to participate in a DDoS attack, and allows them to prove they have done so
 \item Describe a way for target victims to be chosen by consensus of its
@@
 \emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
-resources solving a useless proof-of-work puzzle, such as in Bitcoin, miners are
+resources solving a useless proof-of-work puzzle (such as in Bitcoin), miners are
 instead incentivized to store parts of a large agreed-upon file. In order to be
@@
 day, or equivalently, spend 5 Peercoins that were last spent 2 days ago. Note
-that the holder can send these coins to anyone, including themselves, in order
+that the holder can send these coins to anyone---including themselves---in order
 to consume the coin age.
@@
 from being able to tell if their response would satisfy the target difficulty.
-Otherwise, servers could simply withhold such responses, and no blocks could be
+Otherwise, servers could simply withhold such infrequent responses, and no blocks could be
 published for them.
@@
 
+\section*{Acknowledgements}
+
+The authors are grateful for the support and various discussions on DDoSCoin. We
+thank David Adrian, Matt Bernhard, and Drew Springall for their discussions
+concerning the feasibility of the proof-of-DDoS idea. We also thank the
+anonymous reviewers for their helpful feedback.
+
 {\footnotesize\balance

### 2016-07-25 paper/paper.tex
minor typos pass

@@
 script: a string representing a domain name that the payer wishes to have
-DDoSed, and a target difficulty corresponding to the amount of connections the
+attacked, and a target difficulty corresponding to the amount of connections the
 payer wishes to be made. Once this transaction is stored in a valid block,
@@
 There are a couple important features of this transaction. First, the reason the
-transaction ID of the PAY\_TO\_DDOS transaction is included (committed to) in
+transaction ID of the PAY\_TO\_DDOS transaction is committed to in
 the \texttt{client\_random} is to prevent a client from ``double-claiming''
@@
 and sufficiently difficult proof-of-work
-would indicate to the bounty provider that the target is claiming its bounty.
+could indicate to the bounty provider that the target is claiming its bounty.
 
@@
 
-To evaluate the performance and effectiveness of DDoSCoin, we implement our
+To evaluate the performance and effectiveness of DDoSCoin, we implemented our
 proof-of-DDoS function in 582 lines of C\@. Our mining code uses
@@
 currency via cryptocurrency exchanges. In addition, because DDoSCoin uses
-transactions similar to Bitcoin, trust-less cross-chain transactions can allow
+transactions similar to Bitcoin, trust-less (atomic) cross-chain transactions can allow
 DDoSCoins to be traded for Bitcoins without requiring a trusted 3rd party
@@
 have only ``attacked'' websites we have ownership and authority over.
-Further, we are not publishing a working alt-coin that uses this proof-of-DDoS,
+Furthermore, we are not publishing a working alt-coin that uses this proof-of-DDoS,
 but rather a conceptual description of one.
-We believe it important to fully disclose potential attacks, even those that
+We believe it is important to fully disclose potential attacks, even those that
 require the development of an altcoin to execute. This is especially important in the
@@
 
-The authors are grateful for the support and various discussions on DDoSCoin. We
-thank David Adrian, Matt Bernhard, and Drew Springall for their discussions
-concerning the feasibility of the proof-of-DDoS idea. We also thank the
-anonymous reviewers for their helpful feedback.
+The authors are grateful for the support and various discussions from our
+colleagues on DDoSCoin. In particular, the authors wish to thank David Adrian,
+Matt Bernhard, and Drew Springall for their discussions concerning the
+feasibility of the proof-of-DDoS idea. We also thank the anonymous reviewers
+for their helpful feedback.
 
